---
title: "Maria Figures Final"
description: | 
  Results from Marine Heatwave Simulations 2023
date: "Updated on: `r Sys.Date()`"
format: 
  html:
    toc: true
    self-contained: true
execute: 
  echo: false
  message: ""
  warning: false
---

# About

This markdown contains the code to execute and save figures for Grigoratou et al. 2023


# Loading the Data

Data has been freshly updated in August 2023 to be consistent with an error/bug found in the SST data. 

**Locations to Files:** Here is the link to the resources used to create these figures:

```{r}
#| eval: false
#| echo: false

# https://mercatoroceanfr-my.sharepoint.com/personal/mgrigoratou_mercator-ocean_fr/_layouts/15/onedrive.aspx?id=%2Fpersonal%2Fmgrigoratou%5Fmercator%2Docean%5Ffr%2FDocuments%2FMY%5FPAPERS%2Fplankton%5Fwarmem&ga=1

```

```{r}
#| label: setup-packages
# load packages
library(here)
library(readxl)
library(ggstream)
library(ggforce)
library(tidyverse)
library(gmRi)
library(scales)
library(rcartocolor)
library(patchwork)
library(gt)



# Set theme
theme_set(
  theme_minimal() +
  theme(
    plot.title = element_text(face = "bold",size = 14),
    axis.text = element_text(size = 11),
    axis.title = element_text(size = 12),
    legend.title = element_text(size = 12, face = "bold"),
    legend.text = element_text(size = 11),
    strip.background = element_rect(color = "black"),
    panel.background = element_rect(color = "black"),
    panel.grid.minor = element_blank())
)

# levels for season factors
season_lvls <- c("Winter", "Spring", "Summer", "Autumn")


#
set.seed(123)
```


```{r}
#| label: setup-paths
# Load the Data:
dat_path <- here("maria_data/maria_results_2023/")


# Function to load multiple files at once to a list
load_folder <- function(folder, col_names = TRUE){
  folder_path <- str_c(dat_path, folder)
  fnames <- list.files(folder_path, full.names = TRUE) %>% 
    setNames(str_remove_all(list.files(folder_path), ".csv")) 
  flist <- map(fnames, ~read_csv(.x, guess_max = 1e5, col_types = cols(), col_names = col_names))
  return(flist)
}
  
  

# Function to scale subgroups as a vector
scale_this <- function(x){ (x - mean(x, na.rm=TRUE)) / sd(x, na.rm=TRUE) }


```





```{r}
#| label: setup-factor-levels
# Factor Levels for all figures
# Set the order that the seasons go in for factor levels
season_order <- c("Spring", "Summer", "Autumn", "Winter")
season_abbr_order <- c("Sp", "Su", "A", "W")
hw_season_order <- c("Control", "Spring HW", "Summer HW", "Autumn HW", "Winter HW")



# Load the size bins - accurate but not helpful this way
size_bin_labels <- tribble(
  ~"functional_group", ~"size_bin", ~"bin_label", 
  "Active Copepod",   "sizebin1",   expression("m <"~10^-2), 
  "Active Copepod",   "sizebin2",   expression(10^-2~"\u2264 m <"~10^-1), 
  "Active Copepod",   "sizebin3",   expression(10^-1~"\u2264 m <"~10^0), 
  "Active Copepod",   "sizebin4",   expression(10^0~"\u2264 m <"~10^1), 
  "Active Copepod",   "sizebin5",   expression(10^1~"\u2264 m <"~10^2), 
  "Active Copepod",   "sizebin6",   expression(10^2~"\u2264 m"), 
  "Passive Copepod",  "sizebin1",   expression("m <"~10^-2), 
  "Passive Copepod",  "sizebin2",   expression(10^-2~"\u2264 m <"~10^-1), 
  "Passive Copepod",  "sizebin3",   expression(10^-1~"\u2264 m <"~10^0), 
  "Passive Copepod",  "sizebin4",   expression(10^0~"\u2264 m <"~10^1), 
  "Passive Copepod",  "sizebin5",   expression(10^1~"\u2264 m <"~10^2), 
  "Passive Copepod",  "sizebin6",   expression(10^2~"\u2264 m"), 
  "Protist",          "sizebin1",   expression("m <"~10^-6), 
  "Protist",          "sizebin2",   expression(10^-6~"\u2264 m <"~10^-5), 
  "Protist",          "sizebin3",   expression(10^-5~"\u2264 m <"~10^-4), 
  "Protist",          "sizebin4",   expression(10^-4~"\u2264 m <"~10^-3), 
  "Protist",          "sizebin5",   expression(10^-3~"\u2264 m <"~10^-2), 
  "Protist",          "sizebin6",   expression(10^-2~"\u2264 m")
)

```






```{r}
#| label: join-dom-species

# ----------
# Reshape them, combine, and match to the key

# Function to match and organize the ID's and their biomass values
join_duos <- function(matrix_id){
  
  #matrix_id <- trial_names[1]
  
  # Identify the functional group tested
  matrix_functional_group <- ifelse(
    test = str_detect(matrix_id, "CaA|CaP"), 
    yes = str_sub(matrix_id, 5,7), 
    no = str_sub(matrix_id, 5,5))


  #---- Step 1: Index Matrix
  
  # Start with the ID (index) matrix
  id_x <- id_matrices[[str_c("idx_", matrix_id)]]
  # Get the dimensions
  matrix_dims <- dim(id_x)
  
  
  # Create a row number column
  # flag the major taxa group tested
  id_long <- id_x %>% 
    mutate(row = row_number(), .before = 1) %>% 
    mutate(
      species = case_when(
        matrix_functional_group == "CaA" ~ "act_cop",
        matrix_functional_group == "CaP" ~ "pass_cop",
        matrix_functional_group == "P" ~ "protist"), 
      .after = "row") %>% 
    setNames(
      c("matrix_row", "species", "seasons", str_c("col_", c(1:(matrix_dims[2]-1))))) %>% 
    pivot_longer(names_to = "matrix_col", values_to = "control", cols = starts_with("col_"))
  
  
  #---- Step 2: Absolute Biomass Matrix
  
  # Pull the matching absolute biomass matrix
  abs_x <- abs_matrices[[str_c("abs_", matrix_id)]]
  abs_long <- abs_x %>% 
    mutate(row = row_number(), .before = 1) %>% 
    mutate(species = case_when(
      matrix_functional_group == "CaA" ~ "act_cop",
      matrix_functional_group == "CaP" ~ "pass_cop",
      matrix_functional_group == "P" ~ "protist"), 
      .after = "row") %>% 
    setNames(c("matrix_row", "species", "seasons", str_c("col_", c(1:(matrix_dims[2]-1))))) %>% 
    pivot_longer(
      names_to = "matrix_col", 
      values_to = "absolute_bio", 
      cols = starts_with("col_"))
  
  
  # Join the three matrices together, add the metadata:
  left_join(
    x = id_long, 
    y = abs_long, 
    by = c("matrix_row", "species", "seasons", "matrix_col")) %>% 
  mutate(control = as.character(control)) %>% 
  mutate(trial = matrix_id, .before = "matrix_row") %>% 
  left_join(
    y = species_df, 
    by = c("species", "control")) %>% 
  select(trial, species, matrix_row, matrix_col, control, absolute_bio, everything())

}


```






## Species Data Key


```{r}
# 1. Species Dataframe
species_df <- readxl::read_xlsx(
  path = str_c(dat_path, "species_dataframe_8_temp.xlsx")) %>% 
  mutate(control = as.character(control),
         pft_numb = as.character(pft_numb))
```


## Dominant Species -  Data Wrangle:


Couple data wrangling steps here:
 - make row and column identifiers for what the season was, and what the year was that matches the heatwave trial
 - add one year of control as a lead-in for plots
 - join the control biomass as a column so we can calculate difference and percent difference from what it would be without a heatwave disturbance
 - do some benchmarking against the taxa specific intra-annual fluctuation in biomass





```{r}
#| label: load-dom-species-data

# 2. Dominant Species

# # 2. Load files for the Dominant Species
dom_species <- load_folder("dominant_species")


# Flag the control scenarios
is_control <- which(str_detect(names(dom_species), "_control"))


# Subset into 3 groups
id_matrices  <- dom_species[which(str_detect(names(dom_species), "idx"))]
abs_matrices <- dom_species[which(str_detect(names(dom_species), "abs"))]


# The unique names for the trios
trial_names <- unique(str_sub(names(dom_species), 5, -1))
trial_names <- setNames(trial_names, trial_names)



# Reshape all the experimental trials, joining the three matrices:
#dom_species_long <- trial_names[-c(is_control)] %>% map(join_duos)
dom_species_long <- trial_names %>% map(join_duos)


# 1. Separate Control Conditions from Experiments


# Heatwave Events Only, no Control conditions
dom_spec_hw <- dom_species_long[!str_detect(names(dom_species_long), "control")]


```

Prepare the absolute biomass data for the dominant species:



```{r}
#| label: tidying-dominant-species-hw-info


# Function to strip out control row and label everything:

tidy_dom_species <- function(x){
    x %>% 
    # Strip out that first row that contains the control conditions
      filter(matrix_row > 1) %>% 
      mutate( 
        # Identify what season the heatwave is happening
        hw_season = case_when(
          str_detect(trial, "spring") ~ "Spring HW",
          str_detect(trial, "summer") ~ "Summer HW",
          str_detect(trial, "autumn") ~ "Autumn HW",
          str_detect(trial, "winter") ~ "Winter HW",
          str_detect(trial, "control") ~ "Control"),
        hw_season = factor(hw_season, levels = hw_season_order),
        
        # Label what season the response is occuring in
        seasons = str_remove_all(seasons, "_hw"),
        seasons = ifelse(seasons == "S", "Spring", seasons),
        seasons = ifelse(seasons == "Sp", "Spring", seasons),
        seasons = ifelse(seasons == "Su", "Summer", seasons),
        seasons = ifelse(seasons == "Autmn", "Autumn", seasons),
        seasons = ifelse(seasons == "A", "Autumn", seasons),
        seasons = ifelse(seasons == "W", "Winter", seasons),
        seasons = factor(seasons, level = season_order),
        
        # Clean up the functional group labels
        functional_group = case_when(
          species == "act_cop" ~ "Active Copepod",
          species == "pass_cop" ~ "Passive Copepod",
          species == "protist" ~ "Protist")) %>% 
      # Within each season do row numbers independently to get the year
      mutate(id = str_c(species, control, sep = "-")) %>% 
      complete(matrix_row, id, seasons) %>% 
      group_by(seasons, id) %>% 
      arrange(matrix_row) %>% 
      mutate(year = row_number()) %>% 
      ungroup() %>% 
      # Create a match of the functional group and the control number
      # Scale biomass within each one
      group_by(id) %>% 
      mutate(abs_bio_z = scale_this(absolute_bio)) %>% 
      ungroup()
}





#----------------

# For Experiments, remove the initial condition row
# Then group by season and renumber years
dom_species_hw <- dom_spec_hw %>% 
  map_dfr(tidy_dom_species) %>% 
  drop_na()


```


### Dominant Species - Seasonal Cycle Control

NOTES: Do a similar cleanup to the heatwave results, with some minor tweaks want all the columns to match so they can append. year = 0, hw_season is either none, or we can repeat it 4 times to filter with the data or we can just plop it on top whenever we want it later.


```{r}
#| label: control-cycle-prep

# Control Data prep

#--------------------
# Function to prepare the control cycle for the dominant species data
# Does a similar tidying of strings, and also does some benchmarking against totals for each species
prep_control <- function(x){
  
  # Pull out the control conditions
  dom_spec_ctrl <- x[which(str_detect(names(x), "control"))]
  
  
  
  # Do the same reshaping
  
  # Put all the control data together
  control_all <- bind_rows(dom_spec_ctrl) %>% 
    mutate( 
      hw_season = "Control",
      # Tidy up all the functional group labels
      functional_group = case_when(
        species == "act_cop" ~ "Active Copepod",
        species == "pass_cop" ~ "Passive Copepod",
        species == "protist" ~ "Protist"),
      # Assign the season labels
      seasons = str_remove_all(seasons, "_hw"),
      seasons = str_remove_all(seasons, "_control"),
      seasons = ifelse(seasons == "S", "Spring", seasons),
      seasons = ifelse(seasons == "Sp", "Spring", seasons),
      seasons = ifelse(seasons == "Su", "Summer", seasons),
      seasons = ifelse(seasons == "A", "Autumn", seasons),
      seasons = ifelse(seasons == "W", "Winter", seasons),
      seasons = factor(seasons, level = season_order)) %>% 
    # Within each season, row number independently to get the year
    mutate(
      id = str_c(species, control, sep = "-"),
      year = 0,
      yseason = year + as.numeric(seasons))
  
  
  
  # Add some metrics on how much each taxa's abundance changes
  # Get the difference in abundance from the natural control fluctuations
  # think waveheight, difference between highest and lowest abundance
  control_range <- control_all %>% 
    group_by(id) %>% 
    summarise(
      ctrl_low = min(absolute_bio, na.rm = T),
      ctrl_high = max(absolute_bio, na.rm = T),
      .groups = "keep") %>% 
    mutate(ctrl_range = ctrl_high - ctrl_low)
  
  
  # Join that back in
  control_all <- left_join(
    control_all, 
    control_range, 
    by = "id")
  
  return(control_all)
}


#--------------------------

# Run that for both groups
dom_spec_ctrl <- prep_control(dom_species_long)

```



### Dominant Species Data Wrangling:

**1. Isolate the HW Season Responses:**

```{r}
#| label: ahw-data-prep


# This step isolates what season the heatwave ocurred in, and adjusts the matrix row number so
# that we can calculate the years correctly later

#----------

# 1b. Pull Each Seasonal Heatwave Response
pull_hw_season <- function(dom_species_data, season_x){
  
  # Add integers to the matrix row to reflect what
  # number the season is within a year so they go in order
  season_offsets <- c(
    "Spring HW" = 1, 
    "Summer HW" = 2, 
    "Autumn HW" = 3, 
    "Winter HW" = 4)
  season_offset <- season_offsets[[season_x]]
  
  # Filter Data and offset the row number
  species_x <- dom_species_data %>% 
    filter(hw_season == season_x) %>% 
    mutate(matrix_row = matrix_row + season_offset)
  return(species_x)
  
}




# Make list for each seasonal heatwave dataset:
hw_season_list <- list(
  "Spring HW" = "Spring HW", 
  "Summer HW" = "Summer HW", 
  "Autumn HW" = "Autumn HW", 
  "Winter HW" = "Winter HW")



# Perform the cleanup:
dom_species_seasons <- map(hw_season_list, function(.x){
  pull_hw_season(dom_species_data = dom_species_hw, season_x = .x)
} )


# # Do it again for the dataset with all species
# all_species_seasons <- map(hw_season_list, ~ pull_hw_season(dom_species_data = dom_species_all_hw, season_x = .x))

# # What is happening with the season matching
# all_species_seasons$`Summer HW`  %>% distinct(seasons)

# Results:
# ahw = august heatwave response
# dom_species_seasons = list of each season's responses
```

**2. Lead with 1-Year of Control:**

```{r}
#| label: place-control-before-response


# This step puts one full year of the control cycle ahead of the seasonal hw response so the baseline can be seen as a lead-in

#------------------------

# 1. Inputs:
# dom_species_seasons$`Spring HW`





# 2. Function to throw a year of cotrol conditions in front
attach_control_lead <- function(hw_response, hw_ctrl, hw_season){
  
  
  # 2. Lead with 1 year of control conditions

  # Take one control cycle and slap it in front of the august heatwave data
  # slap 1 year of control in front, drop winter or put it ahead
  # Want to drop some columns that are only in control and not in ahw
  
  
  # Row Ordering for different seasons
  s_order = list(
    "Spring HW" = c(1,2,3,4),
    "Summer HW" = c(4,1,2,3),
    "Autumn HW"  = c(3,4,1,2),
    "Winter HW"  = c(2,3,4,1))
  row_order = s_order[[hw_season]]
  
  
  
  
  # Format the year leader here:
  control_lead <- hw_ctrl %>% 
    select(all_of(which(names(hw_ctrl) %in% names(hw_response)))) %>% 
    mutate(matrix_row = case_when(
      seasons == "Spring" ~ row_order[1], #3,
      seasons == "Summer" ~ row_order[2], #4,
      seasons == "Autumn" ~  row_order[3], #1,
      seasons == "Winter" ~  row_order[4]  #2
      ))
  
  
  
  # Join the 1-year lead to the august heatwave response
  hw_prepped <- control_lead %>% 
    bind_rows(hw_response)
  return(hw_prepped)
  
}



# # Attach the control conditions before the heatwave response:
# ahw_prepped <- attach_control_lead(hw_response = ahw, hw_ctrl =  dom_spec_ctrl, hw_season = "Autumn HW")
# ahw_all_prepped <- attach_control_lead(ahw_all, dom_spec_all_ctrl, hw_season = "Autumn HW")

# HW and Control 
control_and_response <- imap(dom_species_seasons, function(.x, .y){
  attach_control_lead(
    hw_response = .x, 
    hw_ctrl = dom_spec_ctrl, 
    hw_season = .y)
} )


# # Dimensions good? Yea
# dim(ahw_prepped)
# dim(control_and_response$`Autumn HW`)
```


**3. Calculate Difference from Control:**

This step joins the control biomass in so that we can get the difference between biomass at a given time step and the biomass expectation from the control.



```{r}
#| label: difference from control

# This step joins the control in as its own column to track how far away from baseline the values are

#--------- Join control by season to get difference: --------------



# 1. Inputs
# control_and_response

# Year setup debug:

# # Starting situation
# control_and_response$`Spring HW`  %>% 
#   distinct(year, seasons, hw_season) %>% 
#   arrange(seasons, year)
# 
# # Ending Situation - failing for spring (year = 0 x 2)
# control_and_response$`Spring HW` %>% 
#   mutate(
#     year = (plyr::round_any(matrix_row, accuracy = 4, ceiling) / 4) - 1,
#     year = ifelse(hw_season == "Spring HW", year+1, year)) %>% 
#   distinct(year, seasons, hw_season) %>% 
#   arrange(seasons, year)





# 2. Function to join in the control set and get the differences etc.
calc_biomass_change <- function(x, x_ctrl){

  # Join the control values to the results from the trials
  season_diff <- left_join(
    x = x, 
    y = select(
      x_ctrl, id, seasons, 
      ctrl_bio = absolute_bio, ctrl_low, 
      ctrl_high, ctrl_range),
    by = c("id", "seasons"))
  
  
  # Reap the benefits of joining the control information back in:
  season_diff <- season_diff %>% 
    mutate(
      # Set the year using the row
      year = (plyr::round_any(matrix_row, accuracy = 4, ceiling) / 4) - 1, # original
      year = ifelse(hw_season == "Spring HW", year+1, year),
      
      # Set the display order for taxa
      id = fct_reorder2(id, functional_group, temp_opt),
      
      # Set seasonal factor order
      seasons = factor(seasons, levels = season_order),
      
      # Add label to temp opt
      temp_opt = str_c(temp_opt, "C"),
      temp_opt = fct_rev(temp_opt),
      
      # Calculate difference (absolute bio - ctrl_bio)
      abs_bio_diff = absolute_bio - ctrl_bio,
      
      # Some sort of flag for when biomass is back to control conditions?
      diff_percent = (abs_bio_diff/ctrl_bio)*100,
      diff_flag = ifelse(between(diff_percent, -20, 20), "<20% from Control", ">20% from Control"))
  
  
  return(season_diff)

}


```




```{r}
#------- Prep for each seasonal heatwave

# Do it for all the seasons
seasonal_response <- map(
  .x = control_and_response, 
  .f = function(.x){
  calc_biomass_change(
    x = .x, 
    x_ctrl = dom_spec_ctrl)
})


# Dimensions good? Yea
# dim(ahw_diff)
# dim(seasonal_response$`Autumn HW`)
```






# Fig. 1: Abiotic Conditions

The following figures show the annual cycles of abiotoc conditions as their own plots. This is the context for how each seasonal cycle progresses within the year, and what the plankton community are responding to.

```{r}

# Load the Data:
dat_path <- here("maria_data/maria_results_2023/")

#### Column 1: SST-MLD-Nitrogen
abiotic <- read_csv(str_c(dat_path, "control_values/abiotic_control_daily.csv"))


# Reshape
abiot_long <- abiotic %>% 
  pivot_longer(cols = c(temp, MLD, Nitrogen), names_to = "var", values_to = "vals") %>% 
  mutate(
    labels = case_when(
    var == "temp" ~ "Temperature (\u00b0C)",
    var == "MLD"  ~ "Mixed Layer Depth (m)",
    var == "Nitrogen"  ~ "Nitrogen"),
    labels = fct_rev(labels),
    # Start Day 1 at this date and add them forward:
    date = as.Date("2000-12-01") + (day-1),
    szn_mid =  case_when(
      between(date, as.Date("2000-12-01"), as.Date("2001-03-01")) ~ as.Date("2000-12-01")+45,
      between(date, as.Date("2001-03-01"), as.Date("2001-06-01")) ~ as.Date("2001-03-01")+45,
      between(date, as.Date("2001-06-01"), as.Date("2001-09-1")) ~ as.Date("2001-06-01")+45,
      between(date, as.Date("2001-09-01"), as.Date("2001-12-01")) ~ as.Date("2001-09-01")+45,
    )
  ) 



#### Build independent panels
```

::: {.panel-tabset}

### SST

```{r}

# Do them separately, but the same way
abiotic_var <- "temp"
var_dat <- abiot_long %>% filter(var == abiotic_var, day!= 32)
var_means <- var_dat %>% group_by(szn_mid) %>% 
  summarise(mu = str_c("Mean = ", round(mean(vals), 2), "\u00b0C"))

f1_sst <- ggplot(var_dat, aes(date, vals)) +
  geom_line(linewidth  = 1) +
  geom_label(data = var_means, aes(x = szn_mid, y = 13, label = mu)) +
  geom_vline(xintercept = as.Date("2001-02-28"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  geom_vline(xintercept = as.Date("2001-05-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  geom_vline(xintercept = as.Date("2001-08-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  #facet_wrap(~labels, ncol = 1,scales = "free") +
  scale_x_date(breaks = "1 month",  labels = date_format("%b"),
               expand = expansion(add = c(0,0))) +
  labs(
    title = "Sea Surface Temperature",
    x = NULL,  
    y = "Temperature") + 
  scale_y_continuous(labels = number_format(suffix = "\u00b0C"))

f1_sst
  
  
```


### MLD

```{r}
# Do them separately, but the same way
abiotic_var <- "MLD"
var_dat <- abiot_long %>% filter(var == abiotic_var)
var_means <- var_dat %>% group_by(szn_mid) %>% 
  summarise(mu = str_c("Mean = ", round(mean(vals), 2), "m"))


f1_mld <- ggplot(var_dat, aes(date, vals)) +
  geom_line(linewidth  = 1) +
  geom_label(data = var_means, aes(x = szn_mid, y = 22, label = mu)) +
  geom_vline(xintercept = as.Date("2001-02-28"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  geom_vline(xintercept = as.Date("2001-05-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  geom_vline(xintercept = as.Date("2001-08-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  #facet_wrap(~labels, ncol = 1,scales = "free") +
  scale_x_date(breaks = "1 month",  labels = date_format("%b"),
               expand = expansion(add = c(0,0))) +
  labs(
    title = "Mixed Layer Depth",
    x = NULL, 
    y = "Mixed Layer Depth") + 
  scale_y_continuous(labels = number_format(suffix = "m"))

f1_mld
```


### Nitrogen

```{r}

# Do them separately, but the same way
abiotic_var <- "Nitrogen"
var_dat <- abiot_long %>% filter(var == abiotic_var)
var_means <- var_dat %>% group_by(szn_mid) %>% 
  summarise(mu = str_c("Mean = ", round(mean(vals), 2)))


f1_n <- ggplot(var_dat, aes(date, vals)) +
  geom_line(linewidth  = 1) +
  geom_label(data = var_means, aes(x = szn_mid, y = 0, label = mu)) +
  geom_vline(xintercept = as.Date("2001-02-28"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  geom_vline(xintercept = as.Date("2001-05-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  geom_vline(xintercept = as.Date("2001-08-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  #facet_wrap(~labels, ncol = 1,scales = "free") +
  scale_x_date(breaks = "1 month",  labels = date_format("%b"),
               expand = expansion(add = c(0,0))) +
  labs(
    title = "Nitrogen",
    x = "",  
    y = "Nitrogen") + 
  scale_y_continuous(labels = number_format(suffix = "m"))

f1_n

```


### Temp Norms


```{r}
temp_norms <- read_xlsx(here::here("maria_data/maria_results_2023", "temp_norm_adam.xlsx"))

color_levels <- str_c(seq(0,28,4), " ˚C")

# Plot the temperature norms
f1_tnorms <- temp_norms %>% 
  pivot_longer(
    cols = -`ambient Temp`, 
    names_to = "temp_group", 
    values_to = "temp") %>% 
  mutate(temp_group = factor(temp_group, levels = color_levels)) %>% 
  ggplot(aes(`ambient Temp`, temp, group = temp_group)) +
  geom_line(aes(color = temp_group), linewidth  = 1, alpha = 0.8) +
  scale_x_continuous(
    expand = expansion(add = c(0,0)),
    labels = label_number(suffix = "\u00b0C")) +
  scale_y_continuous(labels = label_number(suffix = "\u00b0C")) +
  theme(legend.position = "bottom") +
  scale_color_brewer() +
  guides(
    color = guide_legend(
      nrow = 1, 
      label.position = "bottom", 
      label.hjust = 0.5, 
      keywidth = unit(1.5, "cm"))) +
  labs(
    title = "Temperature Norm",
    x = "Ambient Temperature", 
    y = "Temperature Norm",
    color = "")

f1_tnorms
```




:::



# Fig. 2 Control Conditions

This is a 3 column figure. The left column shows the daily biomass fluctuation cycle. The ccenter column shows the seasonal averages, and the third column displays the biomass for the dominant species.

::: {.panel-tabset}

### Daily Biomass

```{r}
#| label: daily-biomass-streamgraph

####  Column 1: Daily Biomass Streamgraph

# Data
ac_daily <- read_csv(str_c(dat_path, "control_values/Cop_Act_control_daily.csv"))
pc_daily <- read_csv(str_c(dat_path, "control_values/Cop_Pass_control_daily.csv"))
pr_daily <- read_csv(str_c(dat_path, "control_values/P_control_daily.csv"))


# Label Positions for the Seasons
season_position_df <- data.frame(
  dates  = as.Date("1999-12-01") + c(45.625, 136.875, 228.125, 319.375),
  top_pos = rep(Inf, 4),
  bot_pos = rep(-Inf, 4),
  label = c("Winter", "Spring", "Summer", "Autumn")
)

# Y axis labsl
abs_bio_ylab <- expression(paste("Absolute Biomass (mg C ", m^{-3}, ")"))



# # For checking them
# plot(1,1, type = "n")
# text(1,1, expression(10^-2~"\u2264 m <"~10^-1))

# Pivot them longer, Plot
fig2_left_a <- ac_daily %>% 
  pivot_longer(cols = -day, names_to = "size_bin", values_to = "daily_bio") %>% 
  mutate(
    functional_group = "Active Copepod",
    date = as.Date("1999-12-01") + (day-1),
    size_bin = factor(str_remove(size_bin, "sizebin"))) %>% 
  ggplot() +
  geom_area(aes(date, daily_bio, fill = size_bin)) +
  #geom_stream(aes(date, daily_bio, fill = size_bin), type = "ridge", bw = 0.25) +
  geom_vline(xintercept = as.Date("2000-02-29"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = as.Date("2000-05-31"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = as.Date("2000-08-31"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  scale_fill_carto_d(
    palette = "ag_Sunset", direction = -1,
    labels = c(
      expression("           m <"~10^-2),
      expression(10^-2~"\u2264 m <"~10^-1),
      expression(10^-1~"\u2264 m <"~10^0),
      expression(10^0~"\u2264 m <"~10^1),
      expression(10^1~"\u2264 m <"~10^2),
      expression(10^2~"\u2264 m         "))) +
  guides(fill = guide_legend(title = "Copepod\nMass Range", label.hjust = 0.5)) +
  facet_wrap(~functional_group) +
  scale_y_continuous(expand = expansion(add = c(0,0))) +
  scale_x_date(
    breaks = "1 month",  labels = date_format("%b"),
    expand = expansion(add = c(0.5,0.5))) +
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  geom_text(
    data = season_position_df, 
    aes(x = dates, y = bot_pos, label = label), vjust = 3, size = 5) +
  coord_cartesian(
    clip = "off", 
    expand = FALSE, 
    ylim = c(0, 62), 
    xlim = as.Date(c("1999-11-30", "2000-11-30"))) +
  labs(x = NULL, y = NULL, title = "(a.) Daily Biomass")



# Plot passive copepods
fig2_left_b <- pc_daily %>% 
  mutate(sizebin5 = 0.00001, sizebin6 = 0.00001) %>% 
  pivot_longer(cols = -day, names_to = "size_bin", values_to = "daily_bio") %>% 
  mutate(
    functional_group = "Passive Copepod",
    date = as.Date("1999-12-01") + (day-1),
    size_bin = factor(str_remove(size_bin, "sizebin"))) %>% 
  ggplot() +
  geom_area(aes(date, daily_bio, fill = size_bin)) +
  #geom_stream(aes(date, daily_bio, fill = size_bin), type = "ridge", bw = 0.25) +
  geom_vline(xintercept = as.Date("2000-02-28"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = as.Date("2000-05-31"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = as.Date("2000-08-31"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  #scale_fill_brewer(palette = "YlGnBu") +
  scale_fill_carto_d(palette = "ag_Sunset", direction = -1) +
  facet_wrap(~functional_group) +
  scale_y_continuous(expand = expansion(add = c(0,0))) +
  scale_x_date(
    breaks = "1 month",  labels = date_format("%b"),
    expand = expansion(add = c(0.5,0.5))) +
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  geom_text(data = season_position_df, aes(x = dates, y = bot_pos, label = label), vjust = 3, size = 5) +
  coord_cartesian(
    clip = "off", 
    expand = FALSE, 
    ylim = c(0, 62), 
    xlim = as.Date(c("1999-11-30", "2000-11-30"))) +
  labs(x = NULL, y = abs_bio_ylab)




# Plot the Protist Daily Cycle
fig2_left_c <- pr_daily %>% 
  pivot_longer(cols = -day, names_to = "size_bin", values_to = "daily_bio") %>% 
  mutate(
    functional_group = "Protist",
    date = as.Date("1999-12-01") + (day-1),
    size_bin = factor(str_remove(size_bin, "sizebin"))) %>% 
  ggplot() +
  geom_area(aes(date, daily_bio, fill = size_bin)) +
  #geom_stream(aes(date, daily_bio, fill = size_bin), type = "ridge", bw = 0.25) +
  geom_vline(xintercept = as.Date("2000-02-28"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = as.Date("2000-05-31"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = as.Date("2000-08-31"), linetype = 2, color = "gray30", linewidth = 0.75) + 
  scale_fill_brewer(
    palette = "YlGnBu",
    labels = c(
      expression("           m <"~10^-6),
      expression(10^-6~"\u2264 m <"~10^-5),
      expression(10^-5~"\u2264 m <"~10^-4),
      expression(10^-4~"\u2264 m <"~10^-3),
      expression(10^-3~"\u2264 m <"~10^-2),
      expression(10^-2~"\u2264 m         "))) +
  guides(fill = guide_legend(title = "Protist\nMass Range", label.hjust = 0.5)) +
  facet_wrap(~functional_group) +
  scale_y_continuous(expand = expansion(add = c(0,0))) +
  scale_x_date(
    breaks = "1 month",  labels = date_format("%b"),
    expand = expansion(add = c(0.5,0.5))) +
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  geom_text(data = season_position_df, aes(x = dates, y = bot_pos, label = label), vjust = 3, size = 5) +
  coord_cartesian(
    clip = "off", 
    expand = FALSE, 
    ylim = c(0, 135), 
    xlim = as.Date(c("1999-11-30", "2000-11-30"))) +
  labs(x = NULL, y = NULL)

# Assemble them as one stack
#fig2_left_all <- fig2_left_a / fig2_left_b / fig2_left_c + plot_layout(guides = "collect")
fig2_left_all <- fig2_left_a / fig2_left_b / fig2_left_c  & theme(legend.position = "none")
fig2_left_all
```



### Seasonal Biomass

```{r}
# Seasonal Averages: using the seasonal means data from Maria
ac_season <- read_csv(file = str_c(dat_path, "control_values/Cop_Act_control_size_bins_season_mean.csv")) 


# Prep it
ac_season <- ac_season %>% 
  mutate(total = rowSums(across(2:ncol(ac_season)))) %>% 
  pivot_longer(cols = -season, names_to = "size_bin", values_to = "season_bio")  %>% 
  mutate(functional_group = "Active Copepod",
         size_bin = factor(str_remove(size_bin, "sizebin")),
         season = str_to_title(season),
         season = factor(season, levels = season_lvls))

# Passive Copepods
pc_season <- read_csv(file = str_c(dat_path, "control_values/Cop_Pas_control_size_bins_season_mean.csv"))  

# Prep it
pc_season <-  pc_season %>% 
  mutate(sizebin5 = 0.00001, sizebin6 = 0.00001) %>% 
  mutate(total = rowSums(across(2:ncol(pc_season)))) %>% 
  pivot_longer(cols = -season, names_to = "size_bin", values_to = "season_bio")  %>% 
  mutate(functional_group = "Passive Copepod",
         size_bin = factor(str_remove(size_bin, "sizebin")),
         season = str_to_title(season),
         season = factor(season, levels = season_lvls)) 


# Protists
pr_season <- read_csv(file = str_c(dat_path, "control_values/P_control_size_bins_season_mean.csv")) 

# Prep it
pr_season <- pr_season %>% 
  mutate(total = rowSums(across(2:ncol(pr_season)))) %>% 
  pivot_longer(cols = -season, names_to = "size_bin", values_to = "season_bio")  %>% 
  mutate(functional_group = "Protist",
         size_bin = factor(str_remove(size_bin, "sizebin")),
         season = str_to_title(season),
         season = factor(season, levels = season_lvls))




# Active Copepods
f2_mid_a <- ac_season  %>% 
  ggplot() +
  geom_col(aes(season, season_bio, fill = size_bin), position = "dodge", width = 0.75) +
  geom_vline(xintercept = 1.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = 2.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = 3.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  scale_fill_manual(
    #palette = "ag_Sunset", direction = -1,
    values = c(
      "#EDD9A3",
      "#F89F77",
      "#F7667C", 
      "#D43F96", 
      "#932DA3", 
      "#4B2991",
      "gray60"),
    labels = c(
      expression("           m <"~10^-2),
      expression(10^-2~"\u2264 m <"~10^-1),
      expression(10^-1~"\u2264 m <"~10^0),
      expression(10^0~"\u2264 m <"~10^1),
      expression(10^1~"\u2264 m <"~10^2),
      expression(10^2~"\u2264 m         "),
                "Total                  ")) +
  guides(fill = guide_legend(title = "Copepod\nMass Range", label.hjust = 0.5, keyheight = unit(1, "cm"))) +
  facet_wrap(~functional_group) +
  scale_y_continuous(limits = c(0,50), expand = expansion(add = c(0,0))) +
  scale_x_discrete(labels = c("Winter\n(Dec-Feb)", "Spring\n(Mar-May)", "Summer\n(June-Aug)", "Autumn\n(Sept-Nov)")) +
  labs(x = NULL, y = NULL, title = "(b.) Seasonal Mean Biomass")


# Passive Copepods
f2_mid_b <- pc_season %>% 
  ggplot() +
  geom_col(aes(season, season_bio, fill = size_bin), position = "dodge", width = 0.75, show.legend = F) +
  geom_vline(xintercept = 1.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = 2.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = 3.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  #scale_fill_carto_d(palette = "ag_Sunset", direction = -1) +
  scale_fill_manual(
    #palette = "ag_Sunset", direction = -1,
    values = c(
      "#EDD9A3",
      "#F89F77",
      "#F7667C", 
      "#D43F96", 
      "#932DA3", 
      "#4B2991",
      "gray60"
    )) +
  guides(fill = guide_legend(title = "Copepod\nMass Range", label.hjust = 0.5, keyheight = unit(1, "cm"))) +
  facet_wrap(~functional_group) +
  scale_y_continuous(limits = c(0,50), expand = expansion(add = c(0,0))) +
  scale_x_discrete(labels = c("Winter\n(Dec-Feb)", "Spring\n(Mar-May)", "Summer\n(June-Aug)", "Autumn\n(Sept-Nov)")) +
  labs(x = NULL, y = abs_bio_ylab)


# Passive Copepods
f2_mid_c <- pr_season  %>% 
  ggplot() +
  geom_col(aes(season, season_bio, fill = size_bin), position = "dodge", width = 0.75) +
  geom_vline(xintercept = 1.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = 2.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  geom_vline(xintercept = 3.5, linetype = 2, color = "gray30", linewidth = 0.75) + 
  scale_fill_manual(
    values = c(
      "#FFFFCC",
      "#C7E9B4",
      "#7FCDBB",
      "#41B6C4",
      "#2C7FB8",
      "#253494",
      "gray60"),
    labels = c(
      expression("           m <"~10^-6),
      expression(10^-6~"\u2264 m <"~10^-5),
      expression(10^-5~"\u2264 m <"~10^-4),
      expression(10^-4~"\u2264 m <"~10^-3),
      expression(10^-3~"\u2264 m <"~10^-2),
      expression(10^-2~"\u2264 m         "),
                "Total                   ")) +
  guides(fill = guide_legend(title = "Protist\nMass Range", label.hjust = 0.5, keyheight = unit(1, "cm"))) +
  facet_wrap(~functional_group) +
  scale_y_continuous(limits = c(0,110), expand = expansion(add = c(0,0))) +
  scale_x_discrete(labels = c("Winter\n(Dec-Feb)", "Spring\n(Mar-May)", "Summer\n(June-Aug)", "Autumn\n(Sept-Nov)")) +
  labs(x = "Season", 
       y = NULL)



# Assemble
fig2_mid_all <- (f2_mid_a / f2_mid_b + plot_layout(guides = "collect")) /f2_mid_c & theme(legend.position = "left")
fig2_mid_all 

```


:::

## Fig. 2 Complete

```{r}
#| label: fig-control-conditions
#| fig-height: 6
#| fig-width: 12


# # All of them
fig2_full <- fig2_left_all | fig2_mid_all + plot_annotation(title = "Pre-heatwave conditions")
fig2_full 
```






# Fig 3. Size Bin Response
Absolute Biomass concentration anomalies (HW/afterHW – preHW) for the biomass size bins of (a.) protists, (b.) passive and (c.) active copepod feeders for the winter, autumn, spring and summer HW scenarios. 


```{r}
#| label: size-bins-data-prep

# Creates:
# sbins
# sbin_means
# sbin_means_all
# sbin_means_taxa


# 4. Load the Size Bins Data
sbins <- load_folder("size_bins", col_names = FALSE)   %>% 
  imap(function(x,y){
    mutate(x, 
           file_id = y,
           row = row_number(),
           heatwave_condition = case_when(
             row == 1 ~ "Heatwave Occurs",
             row > 1 ~ "Heatwave Recovery"
           )) %>% 
      select(file_id, row, heatwave_condition, everything())
  }) 


# Mean differences
# Process the metadata for the size bin mean biomass table
sbin_mean <- sbins[str_detect(names(sbins), "mean")] %>% 
  map_dfr(function(x){
    ncols <- ncol(x)
    new_names <- c("file_id", "row", "heatwave_condition", str_c("size_bin_", seq(1, ncols-2, 1)))
    new_x <- setNames(x, new_names)
  })



# Split the size bin data based on the file names, which flag which taxa is exposed to a HW
sbin_means_all <- sbin_mean %>% 
  mutate(
    hw_season = case_when(
      str_detect(file_id, "autumn") ~ "Autumn HW",
      str_detect(file_id, "spring") ~ "Spring HW",
      str_detect(file_id, "summer") ~ "Summer HW",
      str_detect(file_id, "winter") ~ "Winter HW"),
    
    # The functional groups that the size bins refer to
    taxa = case_when(
      str_detect(file_id, "cc_A") ~ "Active Copepods",
      str_detect(file_id, "cc_P") ~ "Passive Copepods",
      str_detect(file_id, "P_") ~ "Protists"
    ),
    # Second consideration here:
  # Sometimes only one taxa gets hit with a heatwave "cop_only"
  # Flag those*
    hw_taxa = case_when(
      str_detect(file_id, "cop_only") ~ "Copepods Only",
      str_detect(file_id, "prot_only") ~ "Protists Only",
      TRUE ~ "All Taxa"
    )) %>% 
  # Need to split on file name
  split(.$file_id) %>% 
  
  # This section correctly labels seasons
  map_dfr(function(season_dat){
    
    # Get what season the hw starts on from the file_id
    season_name <- season_dat %>% pull(hw_season)
    season_name <- season_name[1]
    
    # Start on the heatwave and proceed forward
    season_cycle <- switch (season_name,
      "Autumn HW" = c("Autumn", "Winter", "Spring", "Summer"),
      "Winter HW" = c("Winter", "Spring", "Summer", "Autumn"),
      "Spring HW" = c("Spring", "Summer", "Autumn", "Winter"),
      "Summer HW" = c("Summer", "Autumn", "Winter", "Spring"))
    
    # Start on the heatwave and proceed forward
    season_short <- switch (season_name,
      "Autumn HW" = c("A", "W", "Sp", "S"),
      "Winter HW" = c("W", "Sp", "S", "A"),
      "Spring HW" = c("Sp", "S", "A", "W"),
      "Summer HW" = c("S", "A", "W", "Sp"))
    
    # Match rows to seasons
    season_match <- data.frame(
      "row" = 1:36,
      "seasons_cycle" = rep(season_cycle, 9),
      "season_short" = rep(season_short, 9))
    
    # The cycle repeats 9 years
    season_match %>%
      left_join(season_dat, by = "row") %>% 
      mutate(year = (plyr::round_any(row, accuracy = 4, ceiling) / 4))
    
  })


#---------  Reshape Longer

# Reshape longer:
sbin_means_long <- sbin_means_all %>% 
  pivot_longer(
    names_to = "size_bin", 
    values_to = "absolute_biomass", 
    cols = starts_with("size_bin"))



# Make a list for Each Taxa to plot independently
sbin_means_taxa <- sbin_means_long %>% 
  drop_na() %>% 
  mutate(hw_season = factor(
    hw_season, levels = c("Winter HW", "Spring HW", "Summer HW", "Autumn HW")),
    season_short = ifelse(hw_taxa == "Protists Only", season_short, NA),
    season_short = ifelse(size_bin == "size_bin_3", season_short, NA)) %>% 
  split(.$taxa)
```



```{r}
#| label: size-bin-plot-fun

# Plotting Function with controls for limits on color scales and palette choice
size_bin_carto <- function(x, y, plims = c(-8, 8), max_years = 9, palette = "Geyser"){
  
  # Set up color limit labels
  # Set the center as the halfway between absolute min/max
  lim_labs <- c(plims[1], mean(c(0, plims[1])), 0, mean(c(0, plims[2])),  plims[2])
  lim_labs[1] <- str_c("<",lim_labs[1])
  lim_labs[5] <- str_c(">",lim_labs[5])
  
  # Label every four rows for the years
  year_breaks <- seq(1, max_years*4, by = 4) + 2.5
  year_labs <- c(1:length(year_breaks))
  
  
  # And the plot
  x %>% 
    ggplot(aes(row, y = size_bin, fill = absolute_biomass)) +
      geom_tile(linewidth = 0.1, color = "gray") +
      geom_text(aes(x = row+0.5, y = -Inf, label = season_short), vjust = 1.5, size = 2) +
      facet_grid(hw_taxa~hw_season, scales = "free", space = "free") +
      scale_fill_carto_c(
        palette = palette, 
        direction = -1,
        limits = plims,
        labels = lim_labs, 
        oob = oob_squish) +
      scale_x_continuous(
        limits = c(1, (max_years*4)+2),
        breaks = year_breaks, 
        labels = year_labs,
        expand = expansion(add = c(0.5,0.5))) +
    geom_vline(xintercept = 5.5, linetype = 1, color = "gray30", linewidth = 0.75) + 
      geom_vline(xintercept = 9.5, linetype = 1, color = "gray30", linewidth = 0.75) + 
      geom_vline(xintercept = 13.5, linetype = 1, color = "gray30", linewidth = 0.75) + 
      geom_vline(xintercept = 17.5, linetype = 1, color = "gray30", linewidth = 0.75) + 
      guides(
        fill = guide_colourbar(
          title.position = "top", 
          title.hjust = 0.5, 
          barwidth = unit(4, "in"), 
          frame.colour = "black", 
          ticks.colour = "black")) +
    theme(
      legend.position = "bottom", 
      #strip.text.y = element_blank(),
      strip.text.y = element_text(angle = 0),
      panel.grid = element_blank(),
      axis.text.x = element_text(
        vjust = -2, face = "bold", size = 12)) +
    labs(
      x = "\nYears", 
      y = "Biomass Size Bins",
      fill = abs_bio_ylab,
      title = y) 
  }
```



```{r}
# Active Copepod Response
f3_ac <- sbin_means_taxa$`Active Copepods` %>% 
  filter(size_bin %not in% c("size_bin_1", "size_bin_2") ) %>% 
  size_bin_carto(
    ., 
    y = "Active Copepod", 
    plims = c(-4, 4), 
    max_years = 5,
    palette="Tropic") +
  scale_y_discrete(
    labels = c(
      expression(10^-1~"\u2264 m <"~10^0), #3
      expression(10^0~"\u2264 m <"~10^1),  #4
      expression(10^1~"\u2264 m <"~10^2),  #5
      expression(10^2~"\u2264 m"))) +  #6
  labs(title = "(a.) Active Copepod")      
    

#f3_ac
```



```{r}
# Passive Copepod REsponse
f3_pc <- sbin_means_taxa$`Passive Copepods` %>% 
  filter(size_bin %not in% c("size_bin_1") ) %>% 
  size_bin_carto(
    ., 
    y = "Passive Copepod", 
    palette = "Tropic",
    plims = c(-4, 4), 
    max_years = 5) +
  scale_y_discrete(
    labels = c(
      expression(10^-2~"\u2264 m <"~10^-1), #2
      expression(10^-1~"\u2264 m <"~10^0),  #3
      expression(10^0~"\u2264 m <"~10^1)   #4
    )
  ) +
  labs(title = "(b.) Passive Copepod")

#f3_pc
```



```{r}
# Protist Response
f3_pr <- sbin_means_taxa$Protists %>% 
  filter(size_bin %not in% c("size_bin_1") ) %>% 
  size_bin_carto(
    ., 
    y = "Protists", 
    plims = c(-10, 10), 
    max_years = 5,
    palette = "Tropic")  +
  scale_y_discrete(
    labels = c(
      expression(10^-6~"\u2264 m <"~10^-5), #2
      expression(10^-5~"\u2264 m <"~10^-4), #3
      expression(10^-4~"\u2264 m <"~10^-3), #4
      expression(10^-3~"\u2264 m <"~10^-2), #5
      expression(10^-2~"\u2264 m")# 6
      )) +
  labs(title = "(c.) Protist")


#f3_pr
```



```{r}
#| fig-height: 8
#| fig-width: 10
top <- f3_ac + theme(legend.position = "none") 
mid <- f3_pc 
bot <- f3_pr  
f3_all <- ((top/mid)|bot) #+ plot_annotation(tag_levels = list(c("(a.)", "(b.)", "(c.)")))
f3_all

```

 
 
# Fig 3 Seasonal Heatwaves

These focus in on one specific seasonal heatwave. This makes it easier to see progression within one specific season at the expense of being able to see the annual cycles

```{r}

# Plotting Function for the size bin data, with a seasonal heatwave and functional group focus
plot_heatwave_sbin_biomass <-  function(
    x, fgroup, lims, lbase, hw_in = "Autumn HW", title = NULL,  subtitle = NULL, drop_bins = NULL){
  
  
  # Set the order for the season facets to appear
  seas_order <- switch(hw_in,
    "Autumn HW" = c("Autumn", "Winter", "Spring", "Summer"),
    "Winter HW" = c("Winter", "Spring", "Summer", "Autumn"),
    "Spring HW" = c("Spring", "Summer",  "Autumn", "Winter"),
    "Summer HW" = c("Summer", "Autumn", "Winter", "Spring"))
  
  
  
  # Filter the data
  x_filtered <- x %>% filter(
    taxa == fgroup, 
    hw_season == hw_in,
    size_bin %not in% drop_bins ) %>% 
    mutate(seasons_cycle = factor(seasons_cycle, levels = seas_order),
           size_bin = fct_drop(size_bin),
           hw_taxa = case_when(
             hw_taxa == "All Taxa" ~ "HW on all\nplankton groups",
             hw_taxa == "Copepods Only" ~ "HW only\non copepods",
             hw_taxa == "Protists Only" ~ "HW only\non protists"
           ))
  
  # Add a "total" size_bin
  x_total <- x_filtered %>% 
    group_by(year, hw_taxa, seasons_cycle) %>% 
    summarise(absolute_biomass = sum(absolute_biomass, na.rm = T), 
              .groups = "drop")  %>% 
    mutate(size_bin = "size_bin_7")
  
  x_filtered <- full_join(x_filtered, x_total,
                          by = join_by(seasons_cycle, hw_taxa, year, size_bin, absolute_biomass))
  
  
  
   # Make limit labels
  lim_labs <- c(lims[1], mean(c(0, lims[1])), 0, mean(c(0, lims[2])),  lims[2])
  lim_labs[1] <- str_c("<",lim_labs[1])
  lim_labs[5] <- str_c(">",lim_labs[5])
  
  # Build the plot
  ggplot(x_filtered, aes(year, y = size_bin, fill = absolute_biomass)) +
      geom_tile(linewidth = 0.1, color = "gray") +
      facet_grid(hw_taxa~seasons_cycle, scales = "free", space = "free") +
      scale_fill_carto_c(
        palette = "Tropic", 
        direction = -1,
        limits = lims,
        labels = lim_labs, 
        oob = oob_squish) +
      scale_x_continuous(
        breaks = c(1:9), 
        expand = expansion(add = c(0.5,0.5))) +
      guides(
        fill = guide_colourbar(
          title.position = "top", 
          title.hjust = 0.5, 
          barwidth = unit(4, "in"), 
          frame.colour = "black", 
          ticks.colour = "black")) +
    theme(
        plot.title = element_text(face = "bold", size = 14),
        panel.grid = element_blank(),
        strip.text.y = element_text(angle = 0, face = "bold"),
        legend.position = "bottom") +
    labs(x = "Years", 
           y = "Biomass Size Bins",
           fill = abs_bio_ylab,
           title = title,
           subtitle = subtitle) 
  
  
}
```

::: {.panel-tabset}



### Autumn Heatwave

```{r}
# Active Copepods
sb_ahw_ac <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Active Copepods", 
  hw_in = "Autumn HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_2"), 
  title = "(a.) Active Copepod") +
  scale_y_discrete(
    labels = c(
      expression(10^-1~"\u2264 m <"~10^0), #3
      expression(10^0~"\u2264 m <"~10^1), #4
      expression(10^1~"\u2264 m <"~10^2),  #5
      expression(10^2~"\u2264 m"),          #6
      "Total"
    )
  )


# Passive Copepods
sb_ahw_pc <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Passive Copepods", 
  hw_in = "Autumn HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_5", "size_bin_6"), 
  title = "(b.) Passive Copepod")  +
  scale_y_discrete(
    labels = c(
      expression(10^-2~"\u2264 m <"~10^-1), #2
      expression(10^-1~"\u2264 m <"~10^0),  #3
      expression(10^0~"\u2264 m <"~10^1),   #4
      "Total"
    )
  )


# Protists
sb_ahw_pr <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Protists", 
  hw_in = "Autumn HW", 
  lims = c(-10,10), 
  title = "(c.) Protist", 
  drop_bins = c("size_bin_1")) +
  scale_y_discrete(
    labels = c(
      expression(10^-6~"\u2264 m <"~10^-5), #2
      expression(10^-5~"\u2264 m <"~10^-4), #3
      expression(10^-4~"\u2264 m <"~10^-3), #4
      expression(10^-3~"\u2264 m <"~10^-2), #5
      expression(10^-2~"\u2264 m"),# 6
      "Total"
      ))




fig3_ahw <- ((sb_ahw_ac + theme(legend.position = "none")) / sb_ahw_pc) | sb_ahw_pr
fig3_ahw
```



### Winter Heatwave

```{r}
# Active Copepods
sb_whw_ac <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Active Copepods", 
  hw_in = "Winter HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_2"), 
  title = "(a.) Active Copepod") +
  scale_y_discrete(
    labels = c(
      expression(10^-1~"\u2264 m <"~10^0), #3
      expression(10^0~"\u2264 m <"~10^1), #4
      expression(10^1~"\u2264 m <"~10^2),  #5
      expression(10^2~"\u2264 m"),# 6
      "Total"
    )
  )


# Passive Copepods
sb_whw_pc <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Passive Copepods", 
  hw_in = "Winter HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_5", "size_bin_6"), 
  title = "(b.) Passive Copepod")  +
  scale_y_discrete(
    labels = c(
      expression(10^-2~"\u2264 m <"~10^-1), #2
      expression(10^-1~"\u2264 m <"~10^0),  #3
      expression(10^0~"\u2264 m <"~10^1),
      "Total"
    )
  )


# Protists
sb_whw_pr <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Protists", 
  hw_in = "Winter HW", 
  lims = c(-10,10), 
  title = "(c.) Protist", 
  drop_bins = c("size_bin_1")) +
  scale_y_discrete(
    labels = c(
      expression(10^-6~"\u2264 m <"~10^-5), #2
      expression(10^-5~"\u2264 m <"~10^-4), #3
      expression(10^-4~"\u2264 m <"~10^-3), #4
      expression(10^-3~"\u2264 m <"~10^-2), #5
      expression(10^-2~"\u2264 m"),
      "Total"
      ))




fig3_whw <- ((sb_whw_ac + theme(legend.position = "none")) / sb_whw_pc) | sb_whw_pr
fig3_whw
```


### Spring Heatwave

```{r}
# Active Copepods
sb_sphw_ac <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Active Copepods", 
  hw_in = "Spring HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_2"), 
  title = "(a.) Active Copepod") +
  scale_y_discrete(
    labels = c(
      expression(10^-1~"\u2264 m <"~10^0), #3
      expression(10^0~"\u2264 m <"~10^1), #4
      expression(10^1~"\u2264 m <"~10^2),  #5
      expression(10^2~"\u2264 m"),
      "Total"
    )
  )


# Passive Copepods
sb_sphw_pc <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Passive Copepods", 
  hw_in = "Spring HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_5", "size_bin_6"), 
  title = "(b.) Passive Copepod")  +
  scale_y_discrete(
    labels = c(
      expression(10^-2~"\u2264 m <"~10^-1), #2
      expression(10^-1~"\u2264 m <"~10^0),  #3
      expression(10^0~"\u2264 m <"~10^1),
      "Total"
    )
  )


# Protists
sb_sphw_pr <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Protists", 
  hw_in = "Spring HW", 
  lims = c(-10,10), 
  title = "(c.) Protist", 
  drop_bins = c("size_bin_1")) +
  scale_y_discrete(
    labels = c(
      expression(10^-6~"\u2264 m <"~10^-5), #2
      expression(10^-5~"\u2264 m <"~10^-4), #3
      expression(10^-4~"\u2264 m <"~10^-3), #4
      expression(10^-3~"\u2264 m <"~10^-2), #5
      expression(10^-2~"\u2264 m"),
      "Total"
      ))




fig3_sphw <- ((sb_sphw_ac + theme(legend.position = "none")) / sb_sphw_pc) | sb_sphw_pr
fig3_sphw
```


### Summer Heatwave

```{r}
# Active Copepods
sb_shw_ac <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Active Copepods", 
  hw_in = "Summer HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_2"), 
  title = "(a.) Active Copepod") +
  scale_y_discrete(
    labels = c(
      expression(10^-1~"\u2264 m <"~10^0), #3
      expression(10^0~"\u2264 m <"~10^1), #4
      expression(10^1~"\u2264 m <"~10^2),  #5
      expression(10^2~"\u2264 m"),
      "Total"
    )
  )


# Passive Copepods
sb_shw_pc <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Passive Copepods", 
  hw_in = "Summer HW", 
  lims = c(-4,4), 
  drop_bins = c("size_bin_1", "size_bin_5", "size_bin_6"), 
  title = "(b.) Passive Copepod")  +
  scale_y_discrete(
    labels = c(
      expression(10^-2~"\u2264 m <"~10^-1), #2
      expression(10^-1~"\u2264 m <"~10^0),  #3
      expression(10^0~"\u2264 m <"~10^1),
      "Total"
    )
  )


# Protists
sb_shw_pr <- plot_heatwave_sbin_biomass(
  x = sbin_means_long, 
  fgroup = "Protists", 
  hw_in = "Summer HW", 
  lims = c(-10,10), 
  title = "(c.) Protist", 
  drop_bins = c("size_bin_1")) +
  scale_y_discrete(
    labels = c(
      expression(10^-6~"\u2264 m <"~10^-5), #2
      expression(10^-5~"\u2264 m <"~10^-4), #3
      expression(10^-4~"\u2264 m <"~10^-3), #4
      expression(10^-3~"\u2264 m <"~10^-2), #5
      expression(10^-2~"\u2264 m"),
      "Total"
      ))



fig3_shw <- ((sb_shw_ac + theme(legend.position = "none")) / sb_shw_pc) | sb_shw_pr
fig3_shw

```

:::


# Fig 4. Shannon Diversity

 Annual Shannon Diversity Index for (a.) protists, (b.) passive and (c.) active copepod feeders for the winter, spring, autumn and winter HW scenarios.  y axis: years. Year 0: pre-heatwave, Year 1: heatwave (in red) Years 2-9: after-heatwave.  


```{r}

# 3. Shannon Index
shannon_all <- load_folder("shannon_index")  %>% 
  imap(function(x,y){
    mutate(x, file_id = y) %>% 
      pivot_longer(cols = -c(year, file_id), 
                   names_to = "season_taxa", 
                   values_to = "shannon_idx")
  })  %>% bind_rows()


# Supplement the data based on file ID
# There is the season the HW happened and the season that things are happening
shannon_all <- shannon_all %>% 
  mutate(
    # Flag to indicate if that was before or after a heatwave
    hw_status = case_when(
      year == 0 ~ "Pre-Heatwave",
      year == 1 ~ "Heatwave",
      year > 1 ~ "Heatwave Recovery"),
    # Flag for what season the heatwave hit
    hw_season = case_when(
      str_starts(season_taxa, "aut") ~ "Autumn HW",
      str_starts(season_taxa, "spr") ~ "Spring HW",
      str_starts(season_taxa, "win") ~ "Winter HW",
      str_starts(season_taxa, "sum") ~ "Summer HW"),
    hw_season = factor(hw_season,
      levels = hw_season_order),
    # Flag for whatever season the response has occurred
    trial_type = case_when(
      str_detect(season_taxa, "_cop_only") ~ "Copepods Only",
      str_detect(season_taxa, "_prot_only") ~ "Protists Only",
      TRUE ~ "All Taxa"),
    season_trim = str_remove(season_taxa, "_cop_only"),
    season_trim = str_remove(season_trim, "_prot_only"),
    season_trim = str_remove(season_trim, "winter_"),
    season_trim = str_remove(season_trim, "spring_"),
    season_trim = str_remove(season_trim, "summer_"),
    season_trim = str_remove(season_trim, "autumn_"),
    season_trim = str_remove(season_trim, "Cp_"),
    season_trim = str_remove(season_trim, "Ca_"),
    season_trim = str_remove(season_trim, "P_"),
    season = str_to_title(season_trim),
    season = factor(season, levels = 
                      c("Winter", "Spring", "Summer", "Autumn")),
    # Cleaner display text for the functional group impacted
    taxa = case_when(
      str_detect(season_taxa, "Ca_") ~ "Active Copepods",
      str_detect(season_taxa, "Cp_") ~ "Passive Copepods",
      str_detect(season_taxa, "P_")  ~ "Protists")) 


```



```{r}
# make a plot function that can handle the different functional groups
#"#F7FBFF" "#DEEBF7" "#C6DBEF" "#9ECAE1" "#6BAED6" "#4292C6" "#2171B5" "#08519C" "#08306B"
shannon_plot <- function(fgroup, ptitle){
  
  # table for background colors
  
  hw_fill <- c("transparent", "#FDDBC770")
  rect_df <- data.frame(
    hw_status = c("Year 0:\nPre-heatwave\nEquilibrium", "Year 1:\nSeasonal heatwave"),
    xmin = c(-0.5, 0.5),
    xmax = c(0.5, 1.5),
    ymin = rep(-Inf, 2),
    ymax = rep(Inf, 2))
  
  # make the plot
  shannon_all %>% 
    filter(taxa == fgroup) %>% 
    #filter(trial_type == "All HW") %>% 
    ggplot() +
      geom_rect(
        data = rect_df, 
        aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = hw_status), 
        color = "transparent",
        alpha = 0.8) +
    geom_line(
      aes(year, shannon_idx,
          color = trial_type,
          linetype = trial_type), 
      linewidth = 1.2, alpha = 0.7) +
    #scale_color_brewer(palette = "Set1", direction = -1) +
    scale_color_brewer(palette = "Dark2") +
    #scale_color_grey() +
    scale_fill_manual(values = hw_fill) +
    facet_grid(hw_season ~ season) +
    scale_x_continuous(
      breaks = seq(0,5, 1),
      limits = c(0,6),
      labels = 0:5,
      expand = expansion(add = c(0,0))) +
    scale_y_continuous(breaks = seq(0,10, 0.5)) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_rect(fill = NA),
      legend.position = "bottom",
      panel.ontop = TRUE) +
    guides(
      fill = guide_legend(
        title.position = "top", 
        title.hjust = 0.5, 
        override.aes = list(color = "black")),
      linetype = guide_legend(
        title.position = "top", 
        ncol = 3, 
        title.hjust = 0.5,
        override.aes = list(linewidth = 0.8)), 
      color = guide_legend(
        title.position = "top", 
        ncol = 3, 
        title.hjust = 0.5)) +
    labs(title = ptitle,
         x = "Years",
         y = "Shannon Diversity Index",
         color = "Functional Groups Exposed to Heatwave Effect:",
         linetype = "Functional Groups Exposed to Heatwave Effect:",
         fill = "Heatwave Timing:")
}
```


```{r}
#| fig-height: 8
#| fig-width: 10


# Build the figures
shan_ac <- shannon_plot("Active Copepods", "(a.) Active Copepod") 
shan_pc <- shannon_plot("Passive Copepods", "(b.) Passive Copepod") 
shan_pr <- shannon_plot("Protists", "(c.) Protist")


shan_all <- shan_ac + 
  shan_pr + 
  shan_pc + 
  guide_area() + 
  plot_layout(ncol = 2, 
              guides = "collect") & 
  theme(legend.position = "bottom",
        legend.box = "vertical",
        legend.title = element_text(face = "bold", size = 14),
        legend.text = element_text(size = 12))  
shan_all

```






# Fig 5. Dominant Species Biomass

 Absolute seasonal biomass concentration anomalies of the dominant groups of (a.) protists, (b.) passive and (a.) active copepod feeders for the autumn HW scenario during the heatwave and 2 years after the heatwave.   


```{r}
# | label: new-dom-species

# Maria res-supplied these tables for dominant species plots, these should fix
# the problems we were encountering with the reshaped data previously

dom_new_ac <- read_csv(here("maria_data/maria_results_2023/dom_taxa_reshaped/Active_Copepods_Dominant.csv")) %>% 
  select(1:9)
dom_new_pc <- read_csv(here("maria_data/maria_results_2023/dom_taxa_reshaped/Passive_Copepods_Dominant.csv"))
dom_new_pr <- read_csv(here("maria_data/maria_results_2023/dom_taxa_reshaped/Protists_Dominant.csv"))


# Just need to put the control data ahead of the seasons for each to capture starting conditions
# Might be tricky to make sure the taxa_id's go into the right ones

# So annoying dolyr doesn't want to support this function...
named_group_split <- function(.tbl, ...) {
  grouped <- group_by(.tbl, ...)
  names <- rlang::inject(paste(!!!group_keys(grouped), sep = " / "))

  grouped %>% 
    group_split() %>% 
    rlang::set_names(names)
}



# -----------------

# Reassemble them with control out front
dom_new_ac <- dom_new_ac %>% 
  filter(hw_season != "Control") %>% 
  named_group_split(hw_season, season) %>% 
  map_dfr(function(x_grouping){
    
    # Get the details of the group we're appending onto:
    taxa_ids <- unique(x_grouping$taxa_id)
    hw_season_lab <- unique(x_grouping$hw_season)
    season_lab <- unique(x_grouping$season)
    
    # Pull the appropriate control, 
    # filter to the taxa in this group
    # label the hw_season and season so we can facet
    control_bio <- dom_new_ac %>% 
      filter(
        hw_season == "Control",
        taxa_id %in% taxa_ids) %>% 
      mutate(
        #season = season_lab,
        hw_season = hw_season_lab)
    
    # Append it back
    df_out <- bind_rows(control_bio, x_grouping)
    return(df_out)})





# Reassemble them with control out front
dom_new_pc <- dom_new_pc %>% 
  filter(hw_season != "Control") %>% 
  named_group_split(hw_season, season) %>% 
  map_dfr(function(x_grouping){
    
    # Get the details of the group we're appending onto:
    taxa_ids <- unique(x_grouping$taxa_id)
    hw_season_lab <- unique(x_grouping$hw_season)
    season_lab <- unique(x_grouping$season)
    
    # Pull the appropriate control, 
    # filter to the taxa in this group
    # label the hw_season and season so we can facet
    control_bio <- dom_new_pc %>% 
      filter(
        hw_season == "Control",
        taxa_id %in% taxa_ids) %>% 
      mutate(
        #season = season_lab,
        hw_season = hw_season_lab)
    
    # Append it back
    df_out <- bind_rows(control_bio, x_grouping)
    return(df_out)})





# Reassemble them with control out front
dom_new_pr <- dom_new_pr %>% 
  filter(hw_season != "Control") %>% 
  named_group_split(hw_season, season) %>% 
  map_dfr(function(x_grouping){
    
    # Get the details of the group we're appending onto:
    taxa_ids <- unique(x_grouping$taxa_id)
    hw_season_lab <- unique(x_grouping$hw_season)
    season_lab <- unique(x_grouping$season)
    
    # Pull the appropriate control, 
    # filter to the taxa in this group
    # label the hw_season and season so we can facet
    control_bio <- dom_new_pr %>% 
      filter(
        hw_season == "Control",
        taxa_id %in% taxa_ids) %>% 
      mutate(
        #season = season_lab,
        hw_season = hw_season_lab)
    
    # Append it back
    df_out <- bind_rows(control_bio, x_grouping)
    return(df_out)})



```


```{r}
# Function to plot consistently:
plot_dom_response_new <- function(top_species){


  # Display the heatwave element
  # table for background colors
  hw_fill <- c("transparent", "#FDDBC770")
  rect_df <- data.frame(
    hw_status = c("Year 0:\nPre-heatwave\nEquilibrium", "Year 1:\nSeasonal heatwave"),
    xmin = c(-0.5, 0.5),
    xmax = c(0.5, 1.5),
    ymin = rep(-Inf, 2),
    ymax = rep(Inf, 2))


  # Build the Figure
  top_species %>% 
  # dom_new_ac_test %>% 
    mutate(temp_opt = str_c(temp_opt, "C")) %>% 
    ggplot() +
      geom_rect(
          data = rect_df,
          aes(xmin = xmin, xmax = xmax,
              ymin = ymin, ymax = ymax,
              fill = hw_status),
          color = "transparent",
          alpha = 0.9) +
    geom_line(
      aes(year, absolute_bio, group = taxa_id, color = max_size), 
      show.legend = F, 
      linewidth = 0.7, 
      alpha = 0.4) +
    geom_point(
    aes(year, absolute_bio, shape = fct_rev(as.character(temp_opt)), color = max_size), 
    size = 2) +
    scale_shape_manual(
      values = c(
        "16C" = 15,
        "20C" = 16,
        "24C" = 17,
        "28C" = 18)) +
    scale_color_carto_c(
      palette = "ag_Sunset", 
      direction = -1, 
      trans = "log10", 
      labels = label_log(base = 10), 
      breaks = 10^seq(-3, 3, 1),
      limits = 10^c(-3, 3),
      oob = oob_squish) +
    scale_fill_manual(values = hw_fill) +
    scale_x_continuous(
      limits = c(0, 7),
      expand = expansion(add = c(0.5,0.5)),
      breaks = c(0:9)) +
    guides(
      shape = guide_legend(
        title.position = "top", 
        title.hjust = 0.5, 
        override.aes = list(size = 3)),
      color = guide_colorbar(
        title.position = "top", 
        title.hjust = 0.5, 
        barwidth = unit(7, "cm"), 
        ticks.colour = "black", 
        frame.colour = "black"),
      fill = guide_legend(
        title.position = "top", 
        title.hjust = 0.5, 
        keyheight = unit(1, "cm"),
        override.aes = list(color = "black"))) +
    facet_grid(season~hw_season, scales = "free_y") +
    theme(
      legend.position = "bottom",
      panel.grid = element_blank(),
      panel.background = element_rect(color = "black", fill = "transparent")) +
    labs(
      y = expression(paste("Absolute biomass (mg C ", m^{-3}, ")")),
      x = "Year",
      color = "Maximum Body Size",
      shape = "Temperature Optima",
      fill = "Heatwave Timing:"
    )
  
}
  
  
  
# Testing


# (a.) Active Copepod
dom_response_ac <- plot_dom_response_new(
  top_species = dom_new_ac) +
  labs(title = "(a.) Active Copepod Response") + 
    guides(shape = "none")

# (b.) Passive Copepod
dom_response_pc <- plot_dom_response_new(
  top_species = dom_new_pc) +
  labs(title = "(b.) Passive Copepod Response") + 
    guides(shape = "none")

# (c.) Protist
dom_response_pr <- plot_dom_response_new(
  top_species = dom_new_pr) +
  labs(title = "(c.) Protist Response")



# Assemble something
fig_5 <- dom_response_ac  +
  dom_response_pr +
  dom_response_pc +
  guide_area() + 
  plot_layout(
    ncol =2,
    guides = "collect")


fig_5


```



ADAM: 

“Overall, we see an increase in the relative biomass of warmer species during or after each heatwave.”

“For both protists and copepods, heatwaves lead to changes in the relative biomass and order of the dominant groups during and after the heatwave. 

Still, functional groups with temperature norms of 20 ˚C and 24 ˚C dominate the plankton community before, during, and after the heatwaves and between seasons. The community size structure also reflects periodic variations caused by marine heatwaves. However, no consistent pattern emerges across biomass size bins for all heatwave scenarios, revealing the intricate synergy of direct and indirect temperature effects. For years after the heatwaves, the model shows changes in the order of dominant size groups, highlighting that the effect of a seasonal heatwave on the community properties can persist for a long period. However, the re-position of some dominant size groups does not affect the core community size structure.”  




```{r}
#| label: fig-5-error
#| eval: false

# # Pull the top 5/10 dominant species, the first 5 columns
# top_species <- bind_rows(seasonal_response) %>% 
#   filter(matrix_col %in% str_c("col_", c(1:5)))
# 
# 
# # Repeat the control for each season so that we can facet correctly
# top_species <- map_dfr(
#   .x = setNames(season_lvls, season_lvls), 
#   .f = function(.x){
#     top_species %>% 
#       filter(hw_season == "Control") %>% 
#       mutate(hw_season = str_c(.x, " HW"))}) %>% 
#   bind_rows(filter(top_species, hw_season != "Control")) %>% 
#   mutate(hw_season = factor(hw_season, hw_season_order))  %>% 
#   # Remove trials
#   filter(!str_detect(trial, "only"))
#   
# 
# 
# # Additional step:
# # Drop any that are only in the dominant species group for >2 years
# not_dom <- top_species %>% 
#   group_by(functional_group, control, seasons, hw_season) %>% 
#   summarise(n = n()) %>% 
#   arrange(desc(n)) %>% 
#   filter(n <= 3) %>% 
#   mutate(dom_flag = str_c(functional_group, control, seasons, hw_season))
#   
# 
# 
# 
# # Function to plot consistently:
# plot_dom_species_response <- function(top_species){
#   
# 
#   # Display the heatwave element
#   # table for background colors
#   hw_fill <- c("transparent", "#FDDBC770")
#   rect_df <- data.frame(
#     hw_status = c("Year 0:\nPre-heatwave\nEquilibrium", "Year 1:\nSeasonal heatwave"),
#     xmin = c(-0.5, 0.5),
#     xmax = c(0.5, 1.5),
#     ymin = rep(-Inf, 2),
#     ymax = rep(Inf, 2))
# 
# 
#   # Build the Figure
#   top_species %>% 
#     ggplot() +
#       geom_rect(
#           data = rect_df, 
#           aes(xmin = xmin, xmax = xmax, 
#               ymin = ymin, ymax = ymax, 
#               fill = hw_status), 
#           color = "transparent",
#           alpha = 0.9) +
#     geom_line(
#       aes(year, absolute_bio, group = control, color = max_size), 
#       show.legend = F, 
#       linewidth = 0.7, 
#       alpha = 0.4) +
#     geom_point(
#     aes(year, absolute_bio, shape = fct_rev(temp_opt), color = max_size), 
#     size = 2) +
#     scale_shape_manual(
#       values = c(
#         "16C" = 15,
#         "20C" = 16,
#         "24C" = 17,
#         "28C" = 18)) +
#     scale_color_carto_c(
#       palette = "ag_Sunset", 
#       direction = -1, 
#       trans = "log10", 
#       labels = label_log(base = 10), 
#       breaks = 10^seq(-3, 3, 1),
#       limits = 10^c(-3, 3),
#       oob = oob_squish) +
#     scale_fill_manual(values = hw_fill) +
#     scale_x_continuous(
#       limits = c(0, 7),
#       expand = expansion(add = c(0.5,0.5)),
#       breaks = c(0:9)) +
#     guides(
#       shape = guide_legend(
#         title.position = "top", 
#         title.hjust = 0.5, 
#         override.aes = list(size = 3)),
#       color = guide_colorbar(
#         title.position = "top", 
#         title.hjust = 0.5, 
#         barwidth = unit(7, "cm"), 
#         ticks.colour = "black", 
#         frame.colour = "black"),
#       fill = guide_legend(
#         title.position = "top", 
#         title.hjust = 0.5, 
#         keyheight = unit(1, "cm"),
#         override.aes = list(color = "black"))) +
#     facet_grid(seasons~hw_season, scales = "free_y") +
#     theme(
#       legend.position = "bottom",
#       panel.grid = element_blank(),
#       panel.background = element_rect(color = "black", fill = "transparent")) +
#     labs(
#       y = expression(paste("Absolute biomass (mg C ", m^{-3}, ")")),
#       x = "Year",
#       color = "Maximum Body Size",
#       shape = "Temperature Optima",
#       fill = "Heatwave Timing:"
#     )
#   
# }
```


```{r}

#| eval: false

# # (b.) Active Copepod
# dom_response_ac <- plot_dom_species_response(
#   top_species = top_species %>% filter(functional_group == "Active Copepod")) +
#   labs(title = "(a.) Active Copepod Response") + 
#     guides(shape = "none")
# 
# # (c.) Passive Copepod
# dom_response_pc <- plot_dom_species_response(
#   top_species = top_species %>% filter(functional_group == "Passive Copepod")) +
#   labs(title = "(b.) Passive Copepod Response") + 
#     guides(shape = "none")
# 
# # (d.) Protist
# dom_response_pr <- plot_dom_species_response(
#   top_species = top_species %>% filter(functional_group == "Protist")) +
#   labs(title = "(c.) Protist Response")
# 
# 
# 
# # Assemble something
# fig_5 <- dom_response_ac  +
#   dom_response_pr +
#   dom_response_pc +
#   guide_area() + 
#   plot_layout(
#     ncol =2,
#     guides = "collect")
# 
# 
# fig_5

```










# Fig 6. Biomass Anomalies for Differential Exposure 

Biomass anomalies (HW protists or copepods only -  HW on both protists and copepods) for all seasons for the seasonal HWs and the 7 seasons afterwards. X axis: size bins, y axis: absolute biomass anomalies. The median value and the Standard deviation with a boxplot.



```{r}
# This figure highlights the different responses to biomass bins, depending on what is hit with a MHW

# Data comes from... sbin_means_long
# Need to subtract the response by just copepods or protists from the response seen from all taxa exposed



exposure_compare <- sbin_means_long %>% 
  # Filter data to heatwave event and next 7 seasons
  filter(row %in% c(1:8)) %>% 
  # Set factor levels
  mutate(hw_season = factor(
    hw_season, levels = c("Winter HW", "Spring HW", "Summer HW", "Autumn HW"))) %>% 
  select(-c(file_id)) %>% 
  pivot_wider(names_from = hw_taxa, values_from = absolute_biomass) %>% 
  mutate(only_cop_diff = `Copepods Only` - `All Taxa`,
         only_prot_diff = `Protists Only` - `All Taxa`) %>% 
  select(-c("Copepods Only", "Protists Only", `All Taxa`)) %>% 
  pivot_longer(cols = starts_with("Only"), names_to = "exposure_effect", values_to = "diff_from_alltaxa") %>% 
  mutate(
    size_bin = fct_rev(size_bin),
    exposure_effect = ifelse(exposure_effect == "only_cop_diff",
                             "HW Only on Copepods",
                             "HW Only on Protists"))



# Colors from the original plot
#"#4B2991" "#932DA3" "#D43F96" "#F7667C" "#F89F77" "#EDD9A3"
# "#FFFFCC" "#C7E9B4" "#7FCDBB" "#41B6C4" "#2C7FB8" "#253494"
# scale_fill_manual(values = c("#F89F77", "#7FCDBB" ))


```




```{r}
#| eval: true

# Copepods only Response
plimz <- c(-5,5)


# Active Copepods
ac_6 <- exposure_compare %>% 
  filter(taxa == "Active Copepods") %>% 
  mutate(
    size_bin = factor(size_bin),
    size_bin = fct_rev(size_bin))  %>%
  ggplot(aes(x =  diff_from_alltaxa, y = size_bin)) +
  geom_point(aes(color = exposure_effect), show.legend = F,
             position=position_jitterdodge(), alpha = 0.4) +
  geom_boxplot(aes(fill = exposure_effect),outlier.colour = "transparent") +
  scale_y_discrete(
    labels = c(
      expression("           m <"~10^-2),
      expression(10^-2~"\u2264 m <"~10^-1),
      expression(10^-1~"\u2264 m <"~10^0),
      expression(10^0~"\u2264 m <"~10^1),
      expression(10^1~"\u2264 m <"~10^2),
      expression(10^2~"\u2264 m         "))) +
  scale_x_continuous(limits = plimz) +
  scale_color_manual(values = c("#F89F77", "#7FCDBB" ))+
  scale_fill_manual(values = c("#F89F77", "#7FCDBB" ))+
  theme(legend.position = "none") +
  labs(
    x = expression(paste("Absolute biomass anomaly (mg C ", m^{-3}, ")")),
    y = "Body Mass Range",
    fill = "Functional Group Heatwave Exposure",
    title = "(a.) Active Copepod"
  )

#ac_6
```


```{r}
#| eval: true

# Copepods only Response
plimz <- c(-5,5)


# Passive Copepods
pc_6 <- exposure_compare %>% 
  filter(taxa == "Passive Copepods") %>% 
  mutate(
    size_bin = factor(size_bin),
    size_bin = fct_rev(size_bin))  %>% #filter(size_bin %in% c("size_bin_5", "size_bin_6"))
  drop_na(diff_from_alltaxa) %>% 
  ggplot(aes(x =  diff_from_alltaxa, y = size_bin)) +
  geom_point(aes(color = exposure_effect), show.legend = F,
             position=position_jitterdodge(), alpha = 0.4) +
  geom_boxplot(aes(fill = exposure_effect),outlier.colour = "transparent") +
  scale_y_discrete(
    labels = c(
      expression("           m <"~10^-2),
      expression(10^-2~"\u2264 m <"~10^-1),
      expression(10^-1~"\u2264 m <"~10^0),
      expression(10^0~"\u2264 m <"~10^1)#,
      #expression(10^1~"\u2264 m <"~10^2),
      #expression(10^2~"\u2264 m         ")
      
      )) +
  scale_x_continuous(limits = plimz) +
  scale_color_manual(values = c("#F89F77", "#7FCDBB" ))+
  scale_fill_manual(values = c("#F89F77", "#7FCDBB" ))+
  theme(legend.position = "none") +
  labs(
    x = expression(paste("Absolute biomass anomaly (mg C ", m^{-3}, ")")),
    y = "Body Mass Range",
    fill = "Functional Group Heatwave Exposure",
    title = "(b.) Passive Copepod"
  )


```


```{r}
#| eval: true
# Protists only Response
plimz <- c(-8,8)

pr_6 <- exposure_compare %>% 
  filter(taxa == "Protists") %>% 
  mutate(
    size_bin = factor(size_bin),
    size_bin = fct_rev(size_bin))  %>%
  ggplot(aes(x =  diff_from_alltaxa, y = size_bin)) +
  geom_point(aes(color = exposure_effect), show.legend = F,
             position=position_jitterdodge(), alpha = 0.4) +
  geom_boxplot(aes(fill = exposure_effect),outlier.colour = "transparent") +
  scale_y_discrete(
    labels = c(
      expression("           m <"~10^-6),
      expression(10^-6~"\u2264 m <"~10^-5),
      expression(10^-5~"\u2264 m <"~10^-4),
      expression(10^-4~"\u2264 m <"~10^-3),
      expression(10^-3~"\u2264 m <"~10^-2),
      expression(10^-2~"\u2264 m          "))) +
  scale_x_continuous(limits = plimz) +
  scale_color_manual(values = c("#F89F77", "#7FCDBB" ))+
  scale_fill_manual(values = c("#F89F77", "#7FCDBB" ))+
  theme(legend.position = "bottom") +
  labs(
    x = expression(paste("Absolute biomass anomaly (mg C ", m^{-3}, ")")),
    y = "Body Mass Range",
    fill = "Functional Group Heatwave Exposure",
    title = "(c.) Protist"
  )
```

```{r}
#| fig-height: 8
#| fig-width: 10


f6_all <- ( ac_6  / pc_6 )  | pr_6 
f6_all <- f6_all + plot_layout(guides = "collect") & theme(legend.position = "bottom")
f6_all
```



---

# Supplemental Figures


## Fig SM1 Camila Config


### SM1 a.

Absolute biomass size bins concentrations for the pre-heatwave conditions for active and passive copepod feeders and for protists.

```{r}

# Biomass Controls
ca_daily_setup <- read_csv(here::here("maria_data/maria_results_2023/Cop_Act_control_daily_CamilaSetup.csv"))
cp_daily_setup <- read_csv(here::here("maria_data/maria_results_2023/Cop_Pass_control_daily_CamilaSetup.csv"))
p_daily_setup <- read_csv(here::here("maria_data/maria_results_2023/P_control_daily_CamilaSetup.csv"))


# Put them together, prepare to do a ton of data wrangling for size bins...
camila_controls <- bind_rows(
  bind_rows(
  mutate(ca_daily_setup, functional_group = "Active Copepods"),
  mutate(cp_daily_setup, functional_group = "Passive Copepods"),
  mutate(p_daily_setup, functional_group = "Protists")))  %>% 
  pivot_longer(
    cols = starts_with("size"), 
    names_to = "size_bin", 
    values_to = "control_bio") %>% 
  mutate(
    date = as.Date("2000-01-01") + (day-1),
    size_bin = factor(str_remove(size_bin, "sizebin")),
    # Start it in december to match the December cycle above
    new_date = if_else(
      date <= as.Date("2000-12-01"), 
      as.Date(date+lubridate::years(1)), 
      date),
    new_date = as.Date(new_date)) 



# Active Copepods
sm1_a <- camila_controls %>%
  dplyr::filter(functional_group == "Active Copepods") %>% 
  ggplot() +
  geom_area(aes(new_date, control_bio, fill = size_bin)) +
  # geom_vline(
  #   xintercept = as.Date("2001-02-28"), 
  #   linetype = 2, color = "gray30", linewidth = 0.75) + 
  # geom_vline(
  #   xintercept = as.Date("2001-05-31"), 
  #   linetype = 2, color = "gray30", linewidth = 0.75) + 
  # geom_vline(
  #   xintercept = as.Date("2001-08-31"), 
  #   linetype = 2, color = "gray30", linewidth = 0.75) + 
  scale_fill_carto_d(
    palette = "ag_Sunset", direction = -1,
    labels = c(
      expression("           m <"~10^-2),
      expression(10^-2~"\u2264 m <"~10^-1),
      expression(10^-1~"\u2264 m <"~10^0),
      expression(10^0~"\u2264 m <"~10^1),
      expression(10^1~"\u2264 m <"~10^2),
      expression(10^2~"\u2264 m         "))) +
  guides(fill = guide_legend(title = "Copepod\nMass Range", label.hjust = 0.5)) +
  facet_wrap(~functional_group) +
  scale_y_continuous(expand = expansion(add = c(0,0))) +
  scale_x_date(
    breaks = "1 month",  labels = date_format("%b"),
    expand = expansion(add = c(0.5,0.5))) +
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  geom_text(
    data = season_position_df, 
    aes(x = dates+365, y = bot_pos, label = label), vjust = 3, size = 5) +
  coord_cartesian(
    clip = "off", 
    expand = FALSE, 
    ylim = c(0, 40), 
    xlim = as.Date(c("2000-11-30", "2001-11-30"))) +
  labs(x = NULL, y = NULL, title = "(a.) Daily Biomass")




# Passive Copepods
sm1_b <- camila_controls %>%
  dplyr::filter(functional_group == "Passive Copepods") %>% 
  ggplot() +
  geom_area(aes(new_date, control_bio, fill = size_bin)) +
 # geom_vline(
 #    xintercept = as.Date("2001-02-28"), 
 #    linetype = 2, color = "gray30", linewidth = 0.75) + 
 #  geom_vline(
 #    xintercept = as.Date("2001-05-31"), 
 #    linetype = 2, color = "gray30", linewidth = 0.75) + 
 #  geom_vline(
 #    xintercept = as.Date("2001-08-31"), 
 #    linetype = 2, color = "gray30", linewidth = 0.75) + 
  scale_fill_carto_d(
    palette = "ag_Sunset", direction = -1,
    labels = c(
      expression("           m <"~10^-2),
      expression(10^-2~"\u2264 m <"~10^-1),
      expression(10^-1~"\u2264 m <"~10^0),
      expression(10^0~"\u2264 m <"~10^1),
      expression(10^1~"\u2264 m <"~10^2),
      expression(10^2~"\u2264 m         "))) +
  guides(fill = guide_legend(title = "Copepod\nMass Range", label.hjust = 0.5)) +
  facet_wrap(~functional_group) +
  scale_y_continuous(expand = expansion(add = c(0,0))) +
  scale_x_date(
    breaks = "1 month",  labels = date_format("%b"),
    expand = expansion(add = c(0.5,0.5))) +
  theme(plot.margin = unit(c(1,1,2,1), "lines"),
        legend.position = "none") +
  geom_text(
    data = season_position_df, 
    aes(x = dates+365, y = bot_pos, label = label), vjust = 3, size = 5) +
  coord_cartesian(
    clip = "off", 
    expand = FALSE, 
    ylim = c(0, 40), 
    xlim = as.Date(c("2000-11-30", "2001-11-30"))) +
  labs(x = NULL, y = NULL, NULL)



# Protists
sm1_c <- camila_controls %>%
  dplyr::filter(functional_group == "Protists") %>% 
  ggplot() +
  geom_area(aes(new_date, control_bio, fill = size_bin)) +
  # geom_vline(
  #   xintercept = as.Date("2001-02-28"), 
  #   linetype = 2, color = "gray30", linewidth = 0.75) + 
  # geom_vline(
  #   xintercept = as.Date("2001-05-31"), 
  #   linetype = 2, color = "gray30", linewidth = 0.75) + 
  # geom_vline(
  #   xintercept = as.Date("2001-08-31"), 
  #   linetype = 2, color = "gray30", linewidth = 0.75) + 
  scale_fill_manual(
    values = c(
      "#FFFFCC",
      "#C7E9B4",
      "#7FCDBB",
      "#41B6C4",
      "#2C7FB8",
      "#253494",
      "gray60"),
    labels = c(
      expression("           m <"~10^-6),
      expression(10^-6~"\u2264 m <"~10^-5),
      expression(10^-5~"\u2264 m <"~10^-4),
      expression(10^-4~"\u2264 m <"~10^-3),
      expression(10^-3~"\u2264 m <"~10^-2),
      expression(10^-2~"\u2264 m         "),
                "Total                   ")) +
  guides(fill = guide_legend(title = "Protist\nMass Range", label.hjust = 0.5)) +
  facet_wrap(~functional_group) +
  scale_x_date(
    breaks = "1 month",  labels = date_format("%b"),
    expand = expansion(add = c(0.5,0.5))) +
  theme(plot.margin = unit(c(1,1,2,1), "lines")) +
  geom_text(
    data = season_position_df, 
    aes(x = dates+365, y = bot_pos, label = label), vjust = 3, size = 5) +
  coord_cartesian(
    clip = "off", 
    expand = FALSE, 
    ylim = c(0, 135),
    xlim = as.Date(c("2000-11-30", "2001-11-30"))) +
  labs(x = "", y = NULL, title = NULL)
  

# Combine them
sm1_left <- sm1_a / sm1_b /sm1_c + plot_layout(guides = "collect")



```

### SM1 b.


Sea Surface Temperature and Mix Layer Depth (a) as in the present study and (b) as in Serra-Pompei et al. (2020).  Solid line: Sea Surface Temperature and Mix Layer Depth (a) as in the present study. Dash line: Sea Surface Temperature and Mix Layer Depth (a) as in Serra-Pompei et al. (2020). 


```{r}
 # Camila abiotic conditions:
camila_env <- read_xlsx(here::here("maria_data/maria_results_2023/SST_MLD_SerraPompei2020.xlsx")) %>% select(c(1:4)) %>% 
  setNames(c("day", "temp_k", "temp_c", "mld"))

# pivot and add labels
camila_env_long <- camila_env %>% 
  pivot_longer(
    cols = c(temp_k, temp_c, mld), 
    names_to = "var", 
    values_to = "vals") %>% 
  mutate(
    labels = case_when(
    var == "temp_k" ~ "Temperature (\u00b0K)",
    var == "temp_c" ~ "Temperature (\u00b0C)",
    var == "mld"  ~ "Mixed Layer Depth (m)"),
    labels = fct_rev(labels),
    date = as.Date("2000-01-01") + (day-1),
    # Start it in december to match the December cycle above
    new_date = if_else(
      date <= as.Date("2000-12-01"), 
      as.Date(date+lubridate::years(1)), 
      date),
    new_date = as.Date(new_date))
   


# Build the plots
sm1_sst <- abiot_long %>% 
  filter(var == "temp") %>% 
  ggplot(aes(date, vals)) +
  geom_line(linewidth  = 1, linetype = 1) +
  geom_line(
    data = filter(camila_env_long, var == "temp_c"),
    aes(new_date, vals),
    linewidth  = 1, linetype = 2) +
  # geom_vline(xintercept = as.Date("2001-02-28"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  # geom_vline(xintercept = as.Date("2001-05-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  # geom_vline(xintercept = as.Date("2001-08-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  facet_wrap(~labels, ncol = 1,scales = "free") +
  scale_x_date(
    breaks = "1 month",  
    labels = date_format("%b"),
    expand = expansion(add = c(0,0))) +
  labs(
    title = "(b.) Abiotic Conditions",
    x = NULL,  
    y = "Temperature") + 
  scale_y_continuous(labels = number_format(suffix = "\u00b0C"))

#sm1_sst


sm1_mld <- abiot_long %>% 
  filter(var == "MLD") %>% 
  ggplot(aes(date, vals)) +
  geom_line(linewidth  = 1, linetype = 1) +
  geom_line(
    data = filter(camila_env_long, var == "mld"),
    aes(new_date, vals),
    linewidth  = 1, linetype = 2) +
  # geom_vline(xintercept = as.Date("2001-02-28"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  # geom_vline(xintercept = as.Date("2001-05-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  # geom_vline(xintercept = as.Date("2001-08-31"), linetype = 2, color = "gray40", linewidth = 0.5) + 
  facet_wrap(~labels, ncol = 1,scales = "free") +
  scale_x_date(
    breaks = "1 month",  
    labels = date_format("%b"),
    expand = expansion(add = c(0,0))) +
  labs(
    title = NULL,
    x = NULL,  
    y = "Temperature") + 
  scale_y_continuous(labels = number_format(suffix = "m"))

#sm1_mld


# Put them together
sm1_right <- sm1_sst/sm1_mld


```


### SM1 All

```{r}
sm1_full <- sm1_left | sm1_right
sm1_full

```


## Fig SM2 Shannon diveristy

Seasonal Shannon Diversity Index for (a) active and (b) passive copepod feeders and (c) protists for the summer (June- August) heatwave scenarios under the environmental forcing (Sea Surface Temperature and Mix Layer Depth) as in Serra-Pompei et al. (202).  

Seasonal Shannon Diversity Index for: 
 (a) active
 (b) passive copepod feeders and 
 (c) protists for the summer (June- August) heatwave scenarios.  
 
X-axis: years. Year 0: pre-heatwave, Year 1: heatwave (in red) Years 2-9: after-heatwave. 

```{r}

# Read the diversity data
summer_ca <- read_csv(
  here::here("maria_data/maria_results_2023/summer_Ca_all_seasons_CAMILA_envSETUP.csv"))
summer_cp <- read_csv(
  here::here("maria_data/maria_results_2023/summer_Cp_all_seasons_CAMILA_envSETUP.csv"))
summer_p <- read_csv(
  here::here("maria_data/maria_results_2023/summer_P_all_seasons_CAMILA_envSETUP.csv"))

# Load Camilas Diversity data
camila_diversity <- left_join(summer_ca, summer_cp) %>% 
  left_join(summer_p) %>% 
  rename_all(~str_remove(.x, "summer_")) %>% 
  pivot_longer(
    cols = !year,
    names_to = "group",
    values_to = "shannon_index") %>% 
  separate(group, sep = "_", into = c("functional_group", "season")) %>% 
  mutate(
    functional_group = case_when(
      functional_group == "Ca" ~ "Active Copepods",
      functional_group == "Cp" ~ "Passive Copepods",
      functional_group == "P" ~ "Protists"),
    season = str_to_title(season),
    season = factor(season, levels = season_lvls)
  )
  

# heatwave coverage
rect_df <- data.frame(
    hw_status = c("Year 0:\nPre-heatwave\nEquilibrium", "Year 1:\nSeasonal heatwave"),
    xmin = c(-0.5, 0.5),
    xmax = c(0.5, 1.5),
    ymin = rep(-Inf, 2),
    ymax = rep(Inf, 2))
hw_fill <- c("transparent", "#FDDBC770")

# # Make the plot
# sm2 <- camila_diversity %>% 
#   ggplot() +
#   geom_rect(
#       data = rect_df, 
#       aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = hw_status), 
#       color = "transparent",
#       alpha = 0.8) +
#   geom_line(aes(year, shannon_index, linetype = season),
#             linewidth = 1.2, alpha = 0.7) +
#   facet_grid(functional_group ~ ., scales = "free") +
#   scale_x_continuous(
#       breaks = seq(0,5, 1),
#       limits = c(0,6),
#       labels = 0:5,
#       expand = expansion(add = c(0,0))) +
#   scale_fill_manual(values = hw_fill) +
#   guides(
#       fill = guide_legend(
#         title.position = "top", 
#         title.hjust = 0.5, 
#         keyheight = unit(1, "cm"),
#         override.aes = list(color = "black")),
#       linetype = guide_legend(
#         title.position = "top", 
#         title.hjust = 0.5)) +
#   facet_grid() +
#   theme(
#     legend.position = "bottom",
#     panel.grid = element_blank(),
#     panel.background = element_rect(color = "black", fill = "transparent")) +
#   labs(
#       y = "Shannon Index",
#       x = "Year",
#       linetype = "Season:",
#       fill = "Heatwave Timing:"
#     )
# 
# 
# sm2


# Jk make it look like this

sm2 <- ggplot() +
      geom_rect(
        data = rect_df, 
        aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax, fill = hw_status), 
        color = "transparent",
        alpha = 0.8) +
    geom_line(
      data = camila_diversity,
      aes(year, shannon_index,
          color = functional_group,
          linetype = functional_group), 
      linewidth = 1.2, alpha = 0.7) +
    scale_color_brewer(palette = "Dark2") +
    scale_fill_manual(values = hw_fill) +
    facet_grid(. ~ season) +
    scale_x_continuous(
      breaks = seq(0,5, 1),
      limits = c(0,6),
      labels = 0:5,
      expand = expansion(add = c(0,0))) +
    scale_y_continuous(breaks = seq(0,10, 0.5)) +
    theme(
      panel.grid.minor = element_blank(),
      panel.grid.major = element_blank(),
      panel.background = element_rect(fill = NA),
      legend.position = "bottom",
      panel.ontop = TRUE) +
    guides(
      fill = guide_legend(
        title.position = "top", 
        title.hjust = 0.5, 
        override.aes = list(color = "black")),
      linetype = guide_legend(
        title.position = "top", 
        ncol = 3, 
        title.hjust = 0.5,
        override.aes = list(linewidth = 0.8)), 
      color = guide_legend(
        title.position = "top", 
        ncol = 3, 
        title.hjust = 0.5)) +
    labs(#title = ptitle,
         x = "Years",
         y = "Shannon Diversity Index",
         color = "Functional Groups:",
         linetype = "Functional Groups:",
         fill = "Heatwave Timing:")

sm2
```




## Fig SM3 Study Area SST

Figure SM3: Latitudinal and longitudinal coverage of the Mix Layer Depth and Sea Surface Temperature used as environmental forcing in the model. 


```{r}
library(sf)

# Polygons for mapping
new_england <- rnaturalearth::ne_states("united states of america") %>% st_as_sf(crs = 4326)

# Bathymetric Contour Data
bathy <- raster::raster(str_c(cs_path("res","Bathy/"), "ETOPO1/NEShelf_Etopo1_bathy.tiff")) 

# Make a terra copyfor ggplot using tidyterra
elev_terra <- terra::rast(bathy)

# Region Assignment
# Source Andy Pershing: Reference Pershing et al. 2010
mab_slope <- tribble(
    ~"longitude",       ~"latitude",
    -71.07764473940071, 36.98990872585177,
    -70.37294964932077, 37.52560031966651,
    -69.45253157248167, 38.43942715617401,
    -71.437183050666,   39.4320321682425,
    -71.68166910232638, 39.17994200644733,
    -72.19940427054837, 38.89634057442776,
    -72.5014164520112,  38.75453985841798) %>% 
  mutate(area = "MAB Slope") %>% 
  st_as_sf(coords = c("longitude", "latitude"), crs = 4326) %>% 
  group_by(area) %>% 
  summarise() %>% 
  st_cast("POLYGON") %>% 
  st_convex_hull()


# Map of MAB Slope region
sm3 <- ggplot() +
  tidyterra::geom_spatraster_contour(
    data = elev_terra,
    breaks = seq(0,-15000,-100),
    alpha = 0.4) +
  geom_sf(
    data = mab_slope, 
    color = "orange", 
    fill = "orange", 
    alpha = 0.3,
    linewidth = 1,
    linetype = 1) + 
  geom_sf(data = new_england) +
  map_theme() +
  coord_sf(xlim = c(-76.2,-69),
           ylim = c(36, 42.1), 
           expand = T)


sm3

```
 












# Dominant Species Seasonal Responses

```{r}
#| label: figure-3-seasonal-function


# 1. Plotting Function:
# Make a function to plot the different functional groups separately with some plot controls:
plot_abs_diff <- function(x, fgroup, lims, lbase, title = NULL, hw_in){
  
  # Make limit labels
  lim_labs <- c(lims[1], mean(c(0, lims[1])), 0, mean(c(0, lims[2])),  lims[2])
  lim_labs[1] <- str_c("<",lim_labs[1])
  lim_labs[5] <- str_c(">",lim_labs[5])
  
  # Set the order for the season facets to appear
  seas_order <- switch(hw_in,
    "A" = c("Autumn", "Winter", "Spring", "Summer"),
    "W" = c("Winter", "Spring", "Summer", "Autumn"),
    "Sp" = c("Spring", "Summer",  "Autumn", "Winter"),
    "S" = c("Summer", "Autumn", "Winter", "Spring"))
  
  # Prepare the data
  x_plot <- x %>% 
    filter(!temp_opt %in% str_c(c(0, 4, 8, 12, 16), "C")) %>% 
    filter(hw_season != "control") %>% 
    filter(functional_group %in% fgroup) %>% 
    mutate(functional_group = str_replace(functional_group, " ", "\n"),
           seasons = factor(seasons, levels = seas_order)) %>% 
    drop_na()
    
  # Build the plot 
  out_plot <- x_plot %>% 
    ggplot(aes(year, max_size)) +
      geom_tile(aes(fill = abs_bio_diff), color = "black") +
      scale_fill_carto_c(
        palette = "Tropic", 
        direction = -1, 
        limits = lims, 
        labels = lim_labs,
        oob = scales::squish) + 
      scale_y_log10(
        labels = scales::label_log(base = lbase), 
        breaks = breaks_log(base = lbase)) +
      #theme_dark() +
      theme(
        plot.title = element_text(face = "bold", size = 14),
        panel.grid = element_blank(),
        #strip.background = element_rect(fill = "gray30"),
        strip.text.y = element_text(angle = 0, face = "bold"),
        legend.position = "bottom") +
      guides(fill = guide_colorbar(
        title.position = "top", 
        title.hjust = 0.5, 
        barwidth = unit(4, "in"), 
        frame.colour = "black", 
        ticks.colour = "black")) +
      scale_x_continuous(breaks = c(1:10), expand = expansion(add = c(0.5, 0.5))) +
      facet_grid(temp_opt ~ seasons, scales = "free", space = "free") +
      labs(
        x = "Years",
        title = title,
        y = "Max Size (um)", 
        fill = expression(paste("Absolute biomass anomaly (mg C ", m^{-3}, ")")))
  
  out_plot
  
}
```

::: {.panel-tabset}


### Autumn Heatwave

```{r}
#| fig-height: 8
#| fig-width: 10


ahw_ac <- plot_abs_diff(
  x = seasonal_response$`Autumn HW`,
  fgroup = c("Active Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "A",
  title = "Dominant functional groups - Autumn heatwave") +
  labs(title = "(a.) Active Copepod",
       y = "Max Body Size (μm)")


ahw_pc <- plot_abs_diff(
  x = seasonal_response$`Autumn HW`,
  fgroup = c("Passive Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "A") +
  labs(title = "(b.) Passive Copepod",
       y = "Max Body Size (μm)")

ahw_pr <- plot_abs_diff(
  x = seasonal_response$`Autumn HW`,
  fgroup = c("Protist"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "A") +
  labs(title = "(c.) Protist",
       y = "Max Cell Size (μm)")



ahw_all <- ((ahw_ac + theme(legend.position = "none")) / ahw_pc  | ahw_pr ) 
ahw_all

```


### Winter Heatwave

```{r}
#| fig-height: 8
#| fig-width: 10



whw_ac <- plot_abs_diff(
  x = seasonal_response$`Winter HW`,
  fgroup = c("Active Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "W",
  title = "Dominant functional groups - Winter heatwave") +
  labs(title = "(a.) Active Copepod",
       y = "Max Body Size (μm)")


whw_pc <- plot_abs_diff(
  x = seasonal_response$`Winter HW`,
  fgroup = c("Passive Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "W") +
  labs(title = "(b.) Passive Copepod",
       y = "Max Body Size (μm)")

whw_pr <- plot_abs_diff(
  x = seasonal_response$`Winter HW`,
  fgroup = c("Protist"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "W") +
  labs(title = "(c.) Protist",
       y = "Max Cell Size (μm)")



whw_all <- ((whw_ac + theme(legend.position = "none")) / whw_pc  | whw_pr ) 
whw_all

```


### Spring Heatwave

```{r}
#| fig-height: 8
#| fig-width: 10



sphw_ac <- plot_abs_diff(
  x = seasonal_response$`Spring HW`,
  fgroup = c("Active Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "Sp",
  title = "Dominant functional groups - Spring heatwave") +
  labs(title = "(a.) Active Copepod",
       y = "Max Body Size (μm)")


sphw_pc <- plot_abs_diff(
  x = seasonal_response$`Spring HW`,
  fgroup = c("Passive Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "Sp") +
  labs(title = "(b.) Passive Copepod",
       y = "Max Body Size (μm)")

sphw_pr <- plot_abs_diff(
  x = seasonal_response$`Spring HW`,
  fgroup = c("Protist"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "Sp") +
  labs(title = "(c.) Protist",
       y = "Max Cell Size (μm)")



sphw_all <- ((sphw_ac + theme(legend.position = "none")) / sphw_pc  | sphw_pr ) #+ plot_annotation(tag_levels = list(c("(a.)", "(b.)", "(c.)")))
sphw_all
```

### Summer Heatwave


```{r}
#| fig-height: 8
#| fig-width: 10


shw_ac <- plot_abs_diff(
  x = seasonal_response$`Summer HW`,
  fgroup = c("Active Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "S",
  title = "Dominant functional groups - Summer heatwave") +
  labs(title = "(a.) Active Copepod",
       y = "Max Body Size (μm)")


shw_pc <- plot_abs_diff(
  x = seasonal_response$`Summer HW`,
  fgroup = c("Passive Copepod"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "S") +
  labs(title = "(b.) Passive Copepod",
       y = "Max Body Size (μm)")

shw_pr <- plot_abs_diff(
  x = seasonal_response$`Summer HW`,
  fgroup = c("Protist"), 
  lims = c(-1, 1), 
  lbase = 10,
  hw_in = "S") +
  labs(title = "(c.) Protist",
       y = "Max Cell Size (μm)")



shw_all <- ((shw_ac + theme(legend.position = "none")) / shw_pc  | shw_pr )# + plot_annotation(tag_levels = list(c("(a.)", "(b.)", "(c.)")))
shw_all

```


:::


# High-Res Exports

Figures should be cited consecutively in the text by Arabic numerals (Fig. 1, Fig. 2, etc.) and should be grouped together at the end of the paper or in a separate file(s). Legends should be typed double-spaced and grouped at the end of the paper.  

Line and combination figures should preferably be submitted in vector graphics format (e.g. either embedded as vector graphics in a Word document or saved separately in PDF or eps format). If this is not possible, they should be saved separately as pixel-based graphics at 600 dpi at the required print size, and they should be saved in TIFF (not jpg) format or embedded as such in Word. Photographic figures should be saved at 300 dpi in TIFF format, or jpg format with low compression.  

Figures should be drawn/submitted at their smallest practicable size:    
(to fit a single column (82 mm)   
two-thirds page width (110 mm) 
full-page width (173 mm). 

Over-sized figures will be reduced by the Production Editor. If figures are drawn larger than reproduction size, component parts such as symbols and text must be large enough to allow for the necessary reduction. For full instructions on preparing your figures, see our [Electronic Artwork Information for Authors]() page and the [electronic artwork guidelines](). 


```{r}
#| label: saving-figures-pdf
#| eval: false



# Local destination
local_save <- here::here("maria_data/maria_results_2023/hi_res_figures/new/")

# Figure 1: Abiotic Conditions
# These can be single column figures


# Save them

# SST
ggsave(filename = str_c(local_save, "fig1_sst_daily.pdf"), 
       plot = f1_sst, 
       width = 82, 
       height = 62, scale = 2,
       units = "mm",
       dpi = 300)

# MLD
ggsave(filename = str_c(local_save, "fig1_mld_daily.pdf"), 
       plot = f1_mld, 
       width = 82, 
       height = 62, scale = 2,
       units = "mm",
       dpi = 300)

ggsave(filename = str_c(local_save, "fig1_tnorms.pdf"), 
       plot = f1_tnorms, 
       width = 82, 
       height = 62, scale = 2,
       units = "mm",
       dpi = 300)


# Nitrogen
# ggsave(filename = str_c(local_save, "nitrogen_daily.pdf"), 
#        plot = f1_n, 
#        width = 82, 
#        height = 62, scale = 2,
#        units = "mm",
#        dpi = 300)





# Figure 2: Control Conditions
# This is a 2/3  or full page figure

ggsave(filename = str_c(local_save, "figure_2.pdf"), 
       plot = fig2_full, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)





# Figure 3: Size-bin responses

# The one that cycles through seasons within the year
ggsave(filename = str_c(local_save, "figure_3.pdf"), 
       plot = f3_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)


# Then the seasonal responses as heatmaps
ggsave(filename = str_c(local_save, "figure_3_augusthw.pdf"), 
       plot = fig3_ahw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "figure_3_winterhw.pdf"), 
       plot = fig3_whw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "figure_3_springhw.pdf"), 
       plot = fig3_sphw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "figure_3_summerhw.pdf"), 
       plot = fig3_shw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)



# Figure 4: Shannon Diversity Index


ggsave(filename = str_c(local_save, "figure_4_shannon_index.pdf"), 
       plot = shan_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)





# Figure 4: Dominant Species responses

# The all season line plot
ggsave(filename = str_c(local_save, "figure_5_dom_taxa.pdf"), 
       plot = fig_5, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)



# Then the seasonal versions as heatmaps
ggsave(filename = str_c(local_save, "domspecies_augusthw.pdf"), 
       plot = ahw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "domspecies_winterhw.pdf"), 
       plot = whw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "domspecies_springhw.pdf"), 
       plot = sphw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "domspecies_summerhw.pdf"), 
       plot = shw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)








# Figure 6: Biomass Anomalies
ggsave(filename = str_c(local_save, "figure_6_biomass.pdf"), 
       plot = f6_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)



# Figure SM1 - Conditions in Camila's model
ggsave(filename = str_c(local_save, "figure_sm1_camilla_setup.pdf"), 
       plot = sm1_full, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)


# Figure SM2
ggsave(filename = str_c(local_save, "figure_sm2_summer_diversity.pdf"), 
       plot = sm2, 
       scale = 2,
       width = 82, 
       height = 62, 
       units = "mm",
       dpi = 300)



# Figure SM3
ggsave(filename = str_c(local_save, "figure_sm3_midatlantic_area_map.pdf"), 
       plot = sm3 , 
       scale = 2,
       width = 82, 
       height = 62, 
       units = "mm",
       dpi = 300)





```



```{r}
#| label: saving-figures-jpg
#| eval: false

# Local destination
local_save <- here::here("maria_data/maria_results_2023/hi_res_figures/new/")

# Figure 1: Abiotic Conditions
# These can be single column figures


# Save them

# SST
ggsave(filename = str_c(local_save, "fig1_sst_daily.jpg"), 
       plot = f1_sst, 
       width = 82, 
       height = 62, scale = 2,
       units = "mm",
       dpi = 300)

# MLD
ggsave(filename = str_c(local_save, "fig1_mld_daily.jpg"), 
       plot = f1_mld, 
       width = 82, 
       height = 62, scale = 2,
       units = "mm",
       dpi = 300)

ggsave(filename = str_c(local_save, "fig1_tnorms.jpg"), 
       plot = f1_tnorms, 
       width = 82, 
       height = 62, scale = 2,
       units = "mm",
       dpi = 300)


# Nitrogen
# ggsave(filename = str_c(local_save, "nitrogen_daily.jpg"), 
#        plot = f1_n, 
#        width = 82, 
#        height = 62, scale = 2,
#        units = "mm",
#        dpi = 300)





# Figure 2: Control Conditions
# This is a 2/3  or full page figure

ggsave(filename = str_c(local_save, "figure_2.jpg"), 
       plot = fig2_full, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)





# Figure 3: Size-bin responses

# The one that cycles through seasons within the year
ggsave(filename = str_c(local_save, "figure_3.jpg"), 
       plot = f3_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)


# Then the seasonal responses as heatmaps
ggsave(filename = str_c(local_save, "figure_3_augusthw.jpg"), 
       plot = fig3_ahw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "figure_3_winterhw.jpg"), 
       plot = fig3_whw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "figure_3_springhw.jpg"), 
       plot = fig3_sphw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "figure_3_summerhw.jpg"), 
       plot = fig3_shw, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)



# Figure 4: Shannon Diversity Index


ggsave(filename = str_c(local_save, "figure_4_shannon_index.jpg"), 
       plot = shan_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)





# Figure 4: Dominant Species responses

# The all season line plot
ggsave(filename = str_c(local_save, "figure_5_dom_taxa.jpg"), 
       plot = fig_5, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)



# Then the seasonal versions as heatmaps
ggsave(filename = str_c(local_save, "domspecies_augusthw.jpg"), 
       plot = ahw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "domspecies_winterhw.jpg"), 
       plot = whw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "domspecies_springhw.jpg"), 
       plot = sphw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)
ggsave(filename = str_c(local_save, "domspecies_summerhw.jpg"), 
       plot = shw_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)








# Figure 6: Biomass Anomalies


ggsave(filename = str_c(local_save, "figure_6_biomass.jpg"), 
       plot = f6_all, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)



# Figure SM1 - Conditions in Camila's model
ggsave(filename = str_c(local_save, "figure_sm1_camilla_setup.jpg"), 
       plot = sm1_full, 
       scale = 2,
       width = 173, 
       height = 130, 
       units = "mm",
       dpi = 300)


# Figure SM2
ggsave(filename = str_c(local_save, "figure_sm2_summer_diversity.jpg"), 
       plot = sm2, 
       scale = 2,
       width = 82, 
       height = 62, 
       units = "mm",
       dpi = 300)



# Figure SM3
ggsave(filename = str_c(local_save, "figure_sm3_midatlantic_area_map.jpg"), 
       plot = sm3 , 
       scale = 2,
       width = 82, 
       height = 62, 
       units = "mm",
       dpi = 300)

```







```{r}
#| label: fig-5-original
#| eval: false

# Pull the top 5/10 dominant species, the first 5 columns
top_species <- bind_rows(seasonal_response) %>% 
  filter(matrix_col %in% str_c("col_", c(1:5)))


# b. Plot the Active Copepods
top_ac <- top_species %>% 
  filter(
    functional_group == "Active Copepod",
    hw_season != "Control",
    !str_detect(trial, "only")) %>% 
  ggplot(aes(year, absolute_bio)) +
  geom_line(
    aes(group = control, color = max_size), 
    linewidth = 0.6, alpha = 0.8) +
  geom_point(
    aes(shape = fct_rev(temp_opt), color = max_size), 
    size = 2) +
  facet_grid(seasons~hw_season, scales = "free_y") +
  scale_shape_manual(
    values = c(
      "16C" = 15,
      "20C" = 16,
      "24C" = 17,
      "28C" = 18)) +
  scale_color_carto_c(
    palette = "ag_Sunset", 
    direction = -1, 
    trans = "log10", 
    labels = label_log(base = 10), 
    breaks = 10^c(-2, -1, 0, 1,2),
    limits = 10^c(-3, 3),
    oob = oob_squish) +
  scale_x_continuous(expand = expansion(add = c(0,0)),breaks = c(1:9)) +
  guides(
    color = guide_colorbar(
      title.position = "top", 
      title.hjust = 0.5, 
      barwidth = unit(5, "cm"), 
      ticks.colour = "black", 
      frame.colour = "black"),
    shape = guide_legend(
      title.position = "top", 
      title.hjust = 0.5, 
      override.aes = list(size = rep(3, 3)))) +
  theme(legend.position = "bottom",
        panel.background = element_rect(fill = "gray80"),
        panel.grid = element_blank()) +
  labs(
    title = "(a.) Active Copepod",
    y = expression(paste("Absolute biomass (mg C ", m^{-3}, ")")),
    x = "Year",
    color = "Maximum Body Size",
    shape = "Temperature Optima"
  )




# c. Plot those passive jabronis
top_pc <- top_species %>% 
  filter(functional_group == "Passive Copepod",
         hw_season != "Control",
         !str_detect(trial, "only")) %>% 
  ggplot(aes(year, absolute_bio)) +
 geom_line(aes(group = control, color = max_size), 
           linewidth = 0.6, alpha = 0.8) +
  geom_point(aes(shape = fct_rev(temp_opt), color = max_size), size = 2) +
  scale_shape_manual(
    values = c(
      "16C" = 15,
      "20C" = 16,
      "24C" = 17,
      "28C" = 18)) +
  scale_color_carto_c(
    palette = "ag_Sunset", 
    direction = -1, 
    trans = "log10", 
    labels = label_log(base = 10), 
    breaks = 10^c(-2, -1, 0, 1,2),
    limits = 10^c(-3, 3),
    oob = oob_squish) +
  scale_x_continuous(expand = expansion(add = c(0,0)),breaks = c(1:9)) +
  facet_grid(seasons~hw_season, scales = "free_y") +
  guides(
    color = guide_colorbar(title.position = "top", title.hjust = 0.5, barwidth = unit(5, "cm"), ticks.colour = "black", frame.colour = "black"),
    shape = guide_legend(title.position = "top", title.hjust = 0.5, override.aes = list(size = rep(3, 3)))) +
  theme(legend.position = "bottom",
        panel.background = element_rect(fill = "gray80"),
        panel.grid = element_blank()) +
  labs(
    title = "(b.) Passive Copepod",
    y = expression(paste("Absolute biomass (mg C ", m^{-3}, ")")),
    x = "Year",
    color = "Maximum Body Size",
    shape = "Temperature Optima"
  )



# d. Protists
top_pr <- top_species %>% 
  filter(functional_group == "Protist",
         hw_season != "Control",
         !str_detect(trial, "only")) %>% 
  ggplot(aes(year, absolute_bio)) +
  geom_line(aes(group = control, color = max_size), linewidth = 0.6, alpha = 0.6) +
  geom_point(aes(shape = fct_rev(temp_opt), color = max_size), size = 2) +
  scale_shape_manual(
    values = c(
      "16C" = 15,
      "20C" = 16,
      "24C" = 17,
      "28C" = 18)) +
  scale_color_distiller(
    palette = "YlGnBu", 
    direction = -1, 
    trans = "log10", 
    labels = label_log(base = 10), 
    breaks = 10^seq(-6,-2, 1),
    limits = 10^c(-7, -3),
    oob = oob_squish) +
  scale_x_continuous(expand = expansion(add = c(0,0)),breaks = c(1:9)) +
  facet_grid(seasons~hw_season, scales = "free_y") +
  guides(
    color = guide_colorbar(
      title.position = "top", 
      title.hjust = 0.5, 
      barwidth = unit(6, "cm"), 
      ticks.colour = "black", 
      frame.colour = "black"),
    shape = guide_legend(title.position = "top", title.hjust = 0.5, override.aes = list(size = rep(3, 4)))) +
  theme(legend.position = "bottom",
        panel.background = element_rect(fill = "gray80"),
        panel.grid = element_blank()) +
  labs(
    title = "(c.) Protist",
    y = expression(paste("Absolute biomass (mg C ", m^{-3}, ")")),
    x = "Year",
    color = "Maximum Body Size",
    shape = "Temperature Optima"
  )
  


```



```{r}
#| label: fig-5-differences
#| eval: false

# What About differencing:
# Take the biomass in the year before, and see how that changes in time
# Should be close to zero as it nears equilibrium

# What About differencing
top_species %>% 
  mutate(dom_flag = str_c(functional_group, control, seasons, hw_season)) %>% 
  filter(
    dom_flag %in% not_dom$dom_flag == FALSE,
    hw_season == "Summer HW") %>% 
  group_by(dom_flag) %>% 
  arrange(year) %>% 
  mutate(
    bio_diff = absolute_bio - lag(absolute_bio, n = 1),
    bio_diff = ifelse(year == 0, NA, bio_diff),
    .groups = "drop") %>% 
  mutate(hw_action = ifelse(year < 2, "Heatwave Exposure", "Post-Heatwave")) %>% 
  filter(year > 0) %>% 
  ggplot() +
  geom_col(aes(year, bio_diff, group = dom_flag, fill = temp_opt),
    show.legend = T,
    #position = "dodge",
    linewidth = 0.1, alpha = 0.5, color = "white") +
  geom_hline(yintercept = 0, linetype = 1, linewidth = 0.8) +
  facet_grid(
    functional_group~hw_action,
    scales = "free",
    space = "free",
    labeller = labeller(
      hw_action = label_wrap_gen(10),
      functional_group = label_wrap_gen(10))) +
  scale_x_continuous(
    expand = expansion(add = c(0.5,0.5)),
    breaks = c(1:9)) +
  theme(
    legend.position = "bottom",
    panel.grid = element_blank()) +
  labs(
    y = expression(paste("Biomass Change from Year-1 (mg C ", m^{-3}, ")")),
    x = "Year",
    color = "Temperature Optima",
    shape = "Temperature Optima",
    fill = "Temperature Optima:",
    title = "Summer Heatwave Seasonal Biomass Change\nDominant Taxa")

```




