---
title: "Gulf of Maine CPR Survey Community Regime Shifts"
author: "Adam Kemberling"
url: "https://github.com/adamkemberling"
affiliation: "Gulf of Maine Research Institute"
affiliation_url: "https://www.gmri.org"
description: | 
  Does the Zooplankton Community in the Gulf of Maine Show Regime Shift Dynamics
date: "Updated on: `r Sys.Date()`"
format: 
  html:
    toc: true
    self-contained: true
execute: 
  echo: false
  warning: false
  message: false
  comment: ""
  fig-align: center
---

# About:

The goal of this markdown is to investigate whether the zooplankton communities identified by our principal component analysis showcase temporal trends that are consistent with regime shift dynamics.

Regime shifts have been tested for using the methods of Rodionov et al. 2004

The p-value threshold for all tests have been set to p = 0.05
The minimum length (years) for a regime was set to 5 years


In the following figures with a second lower panel, a value of 0 for RSI is indicative that the regime shift test for that year did not pass. Years with RSI values have met the significance threshold given the above parameters.
```{r}
# Load packages
library(rshift)
library(tidyverse)
library(here)
library(gmRi)

# Load the pca data
#New levels for taxa plots, ordered by size with calanus together
species_05 <- c("Calanus I-IV", 
                "Calanus finmarchicus V-VI", 
                "Centropages typicus",
                "Oithona spp.",
                "Para-Pseudocalanus spp.",
                "Metridia lucens",  
                "Euphausiacea spp.")
species_05 <- factor(species_05, levels = species_05)
  

theme_set(theme_minimal())


####  Annual/bi-monthly CPR anomalies  ####


####  Quarterly CPR Data with SST  ####

ccel_boxpath <- gmRi::cs_path("ccel")

# source: 03_new_anoms_quarterly_sst.R
cpr_sst <- read_csv(
  str_c(ccel_boxpath, "Data", "Gulf of Maine CPR", "2020_combined_data", "anomalies_w_quarterlysst.csv", sep = "/"),
  col_types = cols(),
  guess_max = 1e5) %>% 
  mutate(period = ifelse(period == "annual", "Annual", period))



# Add some label formatting using taxa from 2005 paper
cpr_sst <- cpr_sst %>% 
  mutate(taxa = stringr::str_to_sentence(taxa),
         taxa = str_replace_all(taxa, "Para_pseu", "Para-Pseu"),
         taxa = str_replace_all(taxa, "i_iv", "I-IV"),
         taxa = str_replace_all(taxa, "v_vi", "V-VI"),
         taxa = str_replace_all(taxa, "_", " "),
         taxa = str_replace_all(taxa, "spp", "spp."),
         taxa = factor(taxa, levels = species_05)) %>% 
  filter(taxa %in% species_05)
```




### Individual Taxa Regime Shifts

```{r}
# take only annual values
taxa_anoms <- cpr_sst %>% 
  filter(period == "Annual")

# Make a wide one to grab specific taxa easier
taxa_wide <- pivot_wider(taxa_anoms, names_from = "taxa", values_from = "anomaly") %>% select(-c(temp_anomaly, lag_ref, year_ref, lag_temp))

# Plot the timeseries
taxa_anoms %>% 
  ggplot(aes(year, anomaly)) +
  geom_line(linewidth = 1) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.8, alpha = 0.5) +
  facet_wrap(~taxa, ncol = 2) +
  labs(y = "Abundance Anomaly")




```


```{r}


# # Weird that it keeps the other columns and their values
# rshift::Rodionov(data = taxa_anoms, col = "anomaly", time = "year", l = 5, prob = 0.95)
# 
# # Do it on one taxa at a time
# rshift::Rodionov(data = taxa_wide, col = "Calanus I-IV", time = "year", l = 5, prob = 0.95, merge = F)
```


::: {.panel-tabset}


```{r}
taxa_col <- as.character(species_05[[1]])

```

### `r taxa_col`

```{r}

RSI_graph(
  data = rshift::Rodionov(
    data = taxa_wide, 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```


```{r}
taxa_col <- as.character(species_05[[2]])

```

### `r taxa_col`

```{r}

RSI_graph(
  data = rshift::Rodionov(
    data = taxa_wide, 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```


```{r}
taxa_col <- as.character(species_05[[3]])

```

### `r taxa_col`

```{r}

RSI_graph(
  data = rshift::Rodionov(
    data = taxa_wide, 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```


```{r}
taxa_col <- as.character(species_05[[4]])

```

### `r taxa_col`

```{r}

RSI_graph(
  data = rshift::Rodionov(
    data = taxa_wide, 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```


```{r}
taxa_col <- as.character(species_05[[5]])

```

### `r taxa_col`

```{r}

RSI_graph(
  data = rshift::Rodionov(
    data = taxa_wide, 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```


```{r}
taxa_col <- as.character(species_05[[6]])

```

### `r taxa_col`

```{r}

RSI_graph(
  data = rshift::Rodionov(
    data = taxa_wide, 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```


```{r}
taxa_col <- as.character(species_05[[7]])

```

### `r taxa_col`

```{r}

RSI_graph(
  data = rshift::Rodionov(
    data = taxa_wide, 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```


:::


## Zooplankton PC Regime Shifts


```{r}


# Load the Principal Component timeseries
# Source: R/new_anom_analyses/02_new_anoms_pca.R
focal_taxa_pc <- read_csv(here("results_data/cpr_focal_pca_timeseries_period_1961-2017.csv"))

# The paper has pc1 flipped to be consistent in direction with the 2005 paper
focal_taxa_pc$`First Mode` <- focal_taxa_pc$`First Mode` * -1

# Plot the timeseries
focal_taxa_pc %>% 
  pivot_longer(values_to = "pc", names_to = "component_num", cols = contains("Mode")) %>% 
  ggplot(aes(year, pc)) +
  geom_line(aes(color = component_num), linewidth = 1) +
  geom_hline(yintercept = 0, linetype = 2, linewidth = 0.8, alpha = 0.5) +
  scale_color_gmri(reverse = T) +
  theme(legend.position = "bottom") +
  labs(y = "PC Loading", x = "Year")
```



::: {.panel-tabset}


### Principal Component 1 (small zooplankton)

```{r}
# # Is the column name's space causing problems
# focal_taxa_pc$mode1 <- focal_taxa_pc$`First Mode`
# taxa_col <- "mode1"

# Doesn't seem like it
taxa_col <- "First Mode"

RSI_graph(
  data = rshift::Rodionov(
    data = drop_na(focal_taxa_pc), 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")  
```

### Principal Component 2 (large zooplankton)

```{r}
taxa_col <- "Second Mode"
RSI_graph(
  data = rshift::Rodionov(
    data = drop_na(focal_taxa_pc), 
    col = taxa_col, 
    time = "year", 
    l = 5, 
    prob = 0.95, 
    merge = T),
  col = taxa_col, 
  time = "year",
  rsi = "RSI")
```

:::


#### Don't need the buoy data

```{r}

# Load the buoy PCA data that uses the buoy sensor data


# Gappy Buoy data - source: 10_buoy_daily_interpolations
buoy_raw <- read_csv(here("R/new_anom_analyses/derived_data/buoy_pca_raw.csv"),
                     col_types = cols(),
                     guess_max = 1e5)

# Interpolated NA Buoy data - source: 10_buoy_daily_interpolations.R
buoy_i <- read_csv(here("R/new_anom_analyses/derived_data/buoy_pca_interp.csv"),
                   col_types = cols())


```


```{r, results='asis'}
# Use gmri css
gmRi::use_gmri_style_rmd(css_file = "gmri_rmarkdown.css")
```
